---
title: "Power Analysis & Mediation"
author: "Julisa"
date: "2/7/2020"
output: 
  html_document:
    toc: True
    toc_depth: 5
    toc_float: 
      collapsed: False
    number_sections: True
    code_folding: hide
---

# Prepping Data 
```{r libraries_and_dataset}

library(here) #collaboration
library(rio) #import data
library(tidyverse) #Tidy data
library(janitor) #clean-up variables
library(psych) #recoding variables
require(lavaan) #mediation model
library(dplyr) # for selecting variables
library(shiny) # to load in power analysis

data <- import(here("Data", "MMIWG.csv"), setclass = "tbl_df")

```

```{r select_variables}

#Select variables of interest and filter for White respondents

data_tidy <- data %>%
  dplyr::select(Race, Age.r, Gender, Sup_Hash:Sup_Training, NtvInvisibility_1:Invisibility1_18, IN_Violence, RacismMini_1:RacismMini_10, AB_Activists:AB_Laws) %>%
  clean_names() %>%
  filter(race == "3")

data_tidy <- data_tidy[-c(1:21), ] # deleted empty rows

# Not filtering for race for this analysis but if we wanted to, code is below
# %>% filter(race == "3") 


```

Invsibility Composite
```{r invisibility_composite}
# Higher values = greater invisibility

data.in <- data_tidy %>%
  dplyr::rename(ntv_invisibility_7 = invisibility1_13,
         ntv_invisibility_8 = invisibility1_14,
         ntv_invisibility_9 = invisibility1_15,
         ntv_invisibility_10 = invisibility1_16,
         ntv_invisibility_11 = invisibility1_17,
         ntv_invisibility_12 = invisibility1_18)

in.raw <- data.in %>%
  dplyr::select(
    ntv_invisibility_1:ntv_invisibility_12)

in.key <- c(1, -1, 1, 1,
           1, 1, 1, -1,
           1, 1, 1, 1)

in.r <-
  reverse.code(in.key,
               in.raw,
               mini = 1,
               maxi = 7)

invisibility.df <- as.data.frame(in.r)

#Item Analysis:
# psych::alpha(in.df, check.keys = TRUE)

Invisibility <-
  multicon::composite(invisibility.df,
  rel = TRUE,
  nomiss = 0.6)
```

Racism Minimization Composite
```{r race_mini_composite}
racemini.raw <- data_tidy %>%
  dplyr::select(
    racism_mini_1:racism_mini_10)

racemini.key <- c(1, -1, 1, -1, -1,
                  -1, -1, 1, 1, 1)

racemini.r <- reverse.code(racemini.key,
                           racemini.raw,
                           mini = 1,
                           maxi = 7)

racemini.df <- as.data.frame(racemini.r)

RaceMini <-
  multicon::composite(racemini.df, rel = TRUE, nomiss = 0.6)

```

Victim Blaming Composite
```{r vic_blame_composite}
vicblame.raw <- data_tidy %>%
  dplyr::select(
    ab_activists,
    ab_sex_work,
    ab_rez,
    ab_runaways,
    ab_drug,
    ab_criminal
    )

#Took out the key and reverse coding since the direction did not change for any of these values. 

vicblame.df <- as.data.frame(vicblame.raw)

VictimBlaming <- multicon::composite(vicblame.df, rel=TRUE, nomiss = 0.6)
```

Structural Forces Composite
```{r structural_forces_composite}
structuralforces.raw <- data_tidy %>%
  dplyr::select(
    ab_non_native_pers,
    ab_citizens,
    ab_male_worker,
    ab_tribal_police,
    ab_laws,
    ab_society
    )

structuralforces.key <- c(1, 1, 1, 1, 1, -1)

structuralforces.r <- reverse.code(structuralforces.key,
                                structuralforces.raw,
                                mini=1,
                                maxi=7)

structuralforces.df <- as.data.frame(structuralforces.r)

StructuralForces <- multicon::composite(structuralforces.df, rel = TRUE, nomiss=0.6)
```

Support Composite
```{r support_composite}
# Higher values = more support
sup <- data_tidy %>%
  dplyr::select(sup_hash:sup_training)

sup.df <- as.data.frame(sup)

# psych::alpha(sup.df, check.keys = TRUE)

Support <-
  multicon::composite(sup.df,
  rel = TRUE,
  nomiss = 0.6)
```

# Mediation Analysis

## Invisibility Mediation Model 
```{r Invisibility Mediation Model}

var <- data.frame(Support, VictimBlaming, StructuralForces, Invisibility, RaceMini)

in.multipleMediation <- '
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * Invisibility
    VictimBlaming ~ a1 * Invisibility
    StructuralForces ~ a2 * Invisibility
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

in.fit <- sem(model = in.multipleMediation, data = var)
summary(in.fit)    

```

## Racism Minimization Mediation Model
```{r Racism Minimization Mediation Model}

rm.multipleMediation <- '
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * RaceMini
    VictimBlaming ~ a1 * RaceMini
    StructuralForces ~ a2 * RaceMini
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

rm.fit <- sem(model = rm.multipleMediation, data = var)
summary(rm.fit)    

```

## Invisibility to Racism Minimization Mediation Model
```{r}
rm.in.multipleMediation <- '
    RaceMini ~ Invisibility
    VictimBlaming ~ Invisibility
    StructuralForces ~ Invisibility
    Support ~ Invisibility
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * RaceMini
    VictimBlaming ~ a1 * RaceMini
    StructuralForces ~ a2 * RaceMini
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

rm.in.fit <- sem(model = rm.in.multipleMediation, data = var)
summary(rm.in.fit) 
```


# Prep for Power Analysis 

## Correlations needed for Power Analysis
```{r Prep for Power analysis}
var <- data.frame(Support, VictimBlaming, StructuralForces, Invisibility, RaceMini)

(corr <- corr.test(var, use = "pairwise.complete.obs")) # correlations for power analysis
```

## Link to Power Analysis Calculator in Code Below
```{r Power Analysis Calculator}
# runGitHub("mc_power_med", "schoam4") 
# this code takes you to site for power analysis calculator
# here is link - https://schoemanna.shinyapps.io/mc_power_med/
```
