---
title: "Power Analysis & Mediation"
author: "Julisa"
date: "2/7/2020"
output: 
  html_document:
    toc: True
    toc_depth: 5
    toc_float: 
      collapsed: False
    number_sections: True
    code_folding: hide
---

# Prepping Data 
```{r libraries_and_dataset}

library(here) #collaboration
library(rio) #import data
library(tidyverse) #Tidy data
library(janitor) #clean-up variables
library(psych) #recoding variables
require(lavaan) #mediation model
library(dplyr) # for selecting variables
library(shiny) # to load in power analysis

# data <- import(here("Data", "MMIWG.csv"), setclass = "tbl_df")

data <- read.csv("C:/Users/Julisa/Documents/MMIWG/MMIWG/Data/RawData.csv")


```


```{r select_variables}

#Select variables of interest and filter for White respondents

# data_tidy <- data %>%
#  dplyr::select(Race, Age.r, Gender, Sup_Hash:Sup_Training, NtvInvisibility_1:Invisibility1_18, IN_Violence, RacismMini_1:RacismMini_10, AB_Activists:AB_Laws) %>%
#  clean_names() %>%
#  filter(race == "3")

data <- data[-c(1:21), ] # deleted empty rows

data <- data %>% filter(Race == 3)

# Not filtering for race for this analysis but if we wanted to, code is below
# %>% filter(race == "3") 


```

Demographics
```{r Demographics}
# N = 188

# Gender
table(data$Gender)

# Age
mean(data$Age.r, na.rm = TRUE)

```

Invsibility Composite
```{r invisibility_composite}
# Higher values = greater invisibility

data.in <- data %>%
  dplyr::rename(ntv_invisibility_1 = NtvInvisibility_1,
                ntv_invisibility_2 = NtvInvisibility_2,
                ntv_invisibility_3 = NtvInvisibility_3,
                ntv_invisibility_5 = NtvInvisibility_4,
                ntv_invisibility_6 = NtvInvisibility_5,
                ntv_invisibility_7 = NtvInvisibility_6,
                ntv_invisibility_8 = Invisibility1_13,
                ntv_invisibility_9 = Invisibility1_14,
                ntv_invisibility_10 = Invisibility1_15,
                ntv_invisibility_11 = Invisibility1_16,
                ntv_invisibility_12 = Invisibility1_17,
                ntv_invisibility_13 = Invisibility1_18)

in.raw <- data %>%
  dplyr::select(NtvInvisibility_1, 
                NtvInvisibility_2, 
                NtvInvisibility_3,
                NtvInvisibility_4,
                NtvInvisibility_5,
                NtvInvisibility_6,
                Invisibility1_13,
                Invisibility1_14,
                Invisibility1_15,
                Invisibility1_16,
                Invisibility1_17,
                Invisibility1_18)

in.key <- c(1, -1, 1, 1, 1, 
            1, 1, -1, 1, 1, 
            1, 1)

in.r <-
  reverse.code(in.key,
               in.raw,
               mini = 1,
               maxi = 7)

invisibility.df <- as.data.frame(in.r)

#Item Analysis:
# psych::alpha(in.df, check.keys = TRUE)

Invisibility <-
  multicon::composite(invisibility.df,
  rel = TRUE,
  nomiss = 0.6)
```

```{r 3 Factor - #1}

data.in <- data %>%
  dplyr::rename(ntv_invisibility_1 = NtvInvisibility_1,
                ntv_invisibility_2 = NtvInvisibility_2,
                ntv_invisibility_3 = NtvInvisibility_3,
                ntv_invisibility_5 = NtvInvisibility_4,
                ntv_invisibility_6 = NtvInvisibility_5,
                ntv_invisibility_7 = NtvInvisibility_6,
                ntv_invisibility_8 = Invisibility1_13,
                ntv_invisibility_9 = Invisibility1_14,
                ntv_invisibility_10 = Invisibility1_15,
                ntv_invisibility_11 = Invisibility1_16,
                ntv_invisibility_12 = Invisibility1_17,
                ntv_invisibility_13 = Invisibility1_18)

in.raw <- data.in %>%
  dplyr::select(
    ntv_invisibility_1:ntv_invisibility_3, ntv_invisibility_5:ntv_invisibility_13)

in.key <- c(1, -1, 1, 1, 1, 
            1, 1, -1, 1, 1, 
            1, 1)
```


# Determining number of factors to extract
```{r}
ev.in <- eigen(cor(invisibility.df, use = "pairwise.complete.obs"))
ap.in <- parallel(subject=nrow(invisibility.df),var=ncol(invisibility.df),
               rep = 100, cent = .05)
nS.in <- nScree(x=ev.in$values, apparallel = ap.in$eigen$qevpea)
plotnScree(nS.in)
```

# Factor loadings
```{r}
fit.in <- factanal(na.omit(invisibility.df), 3, rotation = "varimax")

print(fit.in, digits = 2, cutoff = .3, sort = TRUE)
```


Racism Minimization Composite
```{r race_mini_composite}
racemini.raw <- data %>%
  dplyr::select(
    RacismMini_1:RacismMini_10)

racemini.key <- c(1, -1, 1, -1, -1,
                  -1, -1, 1, 1, 1)

racemini.r <- reverse.code(racemini.key,
                           racemini.raw,
                           mini = 1,
                           maxi = 7)

racemini.df <- as.data.frame(racemini.r)

RaceMini <-
  multicon::composite(racemini.df, rel = TRUE, nomiss = 0.6)

```

Victim Blaming Composite
```{r vic_blame_composite}
vicblame.raw <- data %>%
  dplyr::select(
    AB_Activists,
    AB_SexWork,
    AB_Rez,
    AB_Runaways,
    AB_Drug,
    AB_Criminal
    )

#Took out the key and reverse coding since the direction did not change for any of these values. 

vicblame.df <- as.data.frame(vicblame.raw)

VictimBlaming <- multicon::composite(vicblame.df, rel=TRUE, nomiss = 0.6)
```

Structural Forces Composite
```{r structural_forces_composite}
structuralforces.raw <- data %>%
  dplyr::select(
    AB_NonNative_pers,
    AB_Citizens,
    AB_MaleWorker,
    AB_TribalPolice,
    AB_Laws,
    AB_Society
    )

structuralforces.df <- as.data.frame(structuralforces.raw)

StructuralForces <- multicon::composite(structuralforces.df, rel = TRUE, nomiss=0.6)

```

Support Composite
```{r support_composite}
# Higher values = more support
sup <- data %>%
  dplyr::select(Sup_Hash:Sup_Training)

sup.df <- as.data.frame(sup)

# psych::alpha(sup.df, check.keys = TRUE)

Support <-
  multicon::composite(sup.df,
  rel = TRUE,
  nomiss = 0.6)
```

# Mediation Analysis

## Invisibility to Racism Minimization Mediation Model
```{r}
var <- data.frame(Support, VictimBlaming, StructuralForces, Invisibility, RaceMini)

rm.in.multipleMediation <- '
    RaceMini ~ Invisibility
    VictimBlaming ~ Invisibility
    StructuralForces ~ Invisibility
    Support ~ Invisibility
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * RaceMini
    VictimBlaming ~ a1 * RaceMini
    StructuralForces ~ a2 * RaceMini
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

rm.in.fit <- sem(model = rm.in.multipleMediation, data = var)
summary(rm.in.fit) 
```

## Invisibility Mediation Model 
```{r Invisibility Mediation Model}

in.multipleMediation <- '
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * Invisibility
    VictimBlaming ~ a1 * Invisibility
    StructuralForces ~ a2 * Invisibility
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

in.fit <- sem(model = in.multipleMediation, data = var)
summary(in.fit)    

```

## Racism Minimization Mediation Model
```{r Racism Minimization Mediation Model}

rm.multipleMediation <- '
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * RaceMini
    VictimBlaming ~ a1 * RaceMini
    StructuralForces ~ a2 * RaceMini
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

rm.fit <- sem(model = rm.multipleMediation, data = var)
summary(rm.fit)    

```

# Prep for Power Analysis 

## Correlations needed for Power Analysis
```{r Prep for Power analysis}
var <- data.frame(Support, VictimBlaming, StructuralForces, Invisibility, RaceMini)

(corr <- corr.test(var, use = "pairwise.complete.obs")) # correlations for power analysis
```

## Link to Power Analysis Calculator in Code Below
```{r Power Analysis Calculator}
# runGitHub("mc_power_med", "schoam4") 
# this code takes you to site for power analysis calculator
# here is link - https://schoemanna.shinyapps.io/mc_power_med/
```
