---
title: "MMIWG_2_05_2020"
author: "Jamie Yellowtail"
date: "2/5/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r libraries_and_dataset}

library(here) #collaboration
library(rio) #import data
library(tidyverse) #Tidy data
library(janitor) #clean-up variables
library(pwr) #power analysis
library(psych) #recoding variables
#install.packages("lavaan")
#install.packages("pwr")
require(lavaan) #madiation model
library(dplyr)

data <- import(here("Data", "MMIWG.csv"), setclass = "tbl_df")

```

```{r select_variables}

#Select variables of interest and filter for White respondents

data_tidy <- data %>%
  dplyr::select(Race, Age.r, Gender, Sup_Hash:Sup_Training, NtvInvisibility_1:Invisibility1_18, IN_Violence, RacismMini_1:RacismMini_10, AB_Activists:AB_Laws) %>%
  clean_names() 

# Not filtering for race for this analysis but if we wanted to, code is below
# %>% filter(race == "3") 


```

```{r descriptive_statistics}
#Age statistics
mean_age <- mean(as.numeric(data_tidy$age_r), na.rm = TRUE) %>% round(2)
sd_age <- sd(as.numeric(data_tidy$age_r), na.rm = TRUE) %>% round(2)
r1_age <- min(as.numeric(data_tidy$age_r), na.rm = TRUE)
n <- nrow(data_tidy)

#Ethnicity
#I'm creating a function that will spit out the percentage of people with a given ethnicity, including a % sign (For the entire data set)
percent_ethn <- function(pos){
  paste(((table(data$Race)[[pos]]/n) *100) %>% round(1), "%", sep = "")}
black <- percent_ethn(1)
asian <- percent_ethn(2)
white <- percent_ethn(3)
hispanic <- percent_ethn(4)
native <- percent_ethn(5)
other <- percent_ethn(6)

#Gender 
percent_gen <- function(pos){
  paste(((table(data_tidy$Gender)[[pos]]/n) *100) %>% round(1), "%", sep = "")}
female <- percent_gen(1)
male <- percent_gen(2) ##### This is wrong! Will come back to it


```


# Support for ending MMIWG (5 point) Composite
```{r support_composite}
# Higher values = more support
sup <- data_tidy %>%
  dplyr::select(sup_hash:sup_training)

sup.df <- as.data.frame(sup)

# psych::alpha(sup.df, check.keys = TRUE)

Support <-
  multicon::composite(sup.df,
  rel = TRUE,
  nomiss = 0.6)
```

#Invisibility Scale Composite
```{r invisibility_composite}
# Higher values = greater invisibility

data.in <- data_tidy %>%
  dplyr::rename(ntv_invisibility_7 = invisibility1_13,
         ntv_invisibility_8 = invisibility1_14,
         ntv_invisibility_9 = invisibility1_15,
         ntv_invisibility_10 = invisibility1_16,
         ntv_invisibility_11 = invisibility1_17,
         ntv_invisibility_12 = invisibility1_18)

in.raw <- data.in %>%
  dplyr::select(
    ntv_invisibility_1:ntv_invisibility_12)

in.key <- c(1, -1, 1, 1,
           1, 1, 1, -1,
           1, 1, 1, 1)

in.r <-
  reverse.code(in.key,
               in.raw,
               mini = 1,
               maxi = 7)

invisibility.df <- as.data.frame(in.r)

#Item Analysis:
# psych::alpha(in.df, check.keys = TRUE)

Invisibility <-
  multicon::composite(invisibility.df,
  rel = TRUE,
  nomiss = 0.6)
```

# Attitudes and Beliefs (3 Factors)

1. Victim Blaming (7-point scale)
_Higher scores indicate more victim blaming_
+ MMIWG are not as big of a problem as activists would like people to think.
+ MMIWG were involved in sex work.
+ MMIWG only takes place on the reservation.
+ MMIWG under 18 were runaways.
+ MMIWG were using drugs and/or alcohol.
+ MMIWG were involved in criminal activity.

```{r vic_blame_composite}
vicblame.raw <- data_tidy %>%
  dplyr::select(
    ab_activists,
    ab_sex_work,
    ab_rez,
    ab_runaways,
    ab_drug,
    ab_criminal
    )

#Took out the key and reverse coding since the direction did not change for any of these values. 

vicblame.df <- as.data.frame(vicblame.raw)

VictimBlaming <- multicon::composite(vicblame.df, rel=TRUE, nomiss = 0.6)
```

2. Structural forces and outside factors (7-point scale)
_Higher scores take into account more structural forces_
+ MMIWG are a result of violence perpetrated by non-Natives.
+ Ending the MMIWG crisis is the responsibility of all U.S. citizens.
+ Non-native male workers that live near reservations contribute to the high rates of  MMIWG.
+ Tribal police forces do not have the resources to prevent Native women from being murdered and going missing.
+ Policies and laws that make it difficult to prosecute Non-native offenders contribute to the epidemic of MMIWG.
+ Native women are murdered and go missing because U.S. society does not value Native women.
```{r structural_forces_composite}
structuralforces.raw <- data_tidy %>%
  dplyr::select(
    ab_non_native_pers,
    ab_citizens,
    ab_male_worker,
    ab_tribal_police,
    ab_laws,
    ab_society
    )

structuralforces.key <- c(1, 1, 1, 1, 1, -1)

structuralforces.r <- reverse.code(structuralforces.key,
                                structuralforces.raw,
                                mini=1,
                                maxi=7)

structuralforces.df <- as.data.frame(structuralforces.r)

StructuralForces <- multicon::composite(structuralforces.df, rel = TRUE, nomiss=0.6)
```

Racism Minimization
_Higher scores indicate more racism minimization_
+ Enter Racism Minimization items
```{r race_mini_composite}
racemini.raw <- data_tidy %>%
  dplyr::select(
    racism_mini_1:racism_mini_10)

racemini.key <- c(1, -1, 1, -1, -1,
                  -1, -1, 1, 1, 1)

racemini.r <- reverse.code(racemini.key,
                           racemini.raw,
                           mini = 1,
                           maxi = 7)

racemini.df <- as.data.frame(racemini.r)

RaceMini <-
  multicon::composite(racemini.df, rel = TRUE, nomiss = 0.6)

view(RaceMini)
```


```{r }
var <- data.frame(Support, VictimBlaming, StructuralForces, Invisibility, RaceMini)

(corr <- round(cor(var),2))

X <- var$Support
M1 <- var$VictimBlaming
M2 <- var$StructuralForces
Y <- var$Invisibility

mediate.data <- data.frame(X = X, Y = X, M1 = M1, M2 = M2)

multipleMediation <- '
    Y ~ b1 * M1 + b2 * M2 + c * X
    M1 ~ a1 * X
    M2 ~ a2 * X
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    M1 ~~ M2 
'
fit <- sem(model = multipleMediation, data = mediate.data)
summary(fit)
```


#Linear models

```{r}
knowledge.model <- lm(Support ~ 1 + MMIWG, data = Supp)

summary(knowledge.model)
```


```{r}
Supp <- data.frame(Support, Invisibility, MMIWG)

support.model <- lm(Support ~ 1 + Invisibility, data = Supp)

summary(support.model)
```

