---
title: "EFA_invisibility"
author: "Julisa"
date: "3/30/2020"
output: html_document
---

```{r Loading packages}

library(here) #collaboration
library(rio) #import data
library(tidyverse) #Tidy data
library(janitor) #clean-up variables
library(psych) #recoding variables
require(lavaan) #mediation model
library(dplyr) # for selecting variables
library(shiny) # to load in power analysis
library(hablar)
library(parallel)
library(GPArotation)

```

```{r Tidying dataset}

# loading in raw data set
data <- read.csv("C:/Users/Julisa/Documents/MMIWG/MMIWG/Data/RawData.csv", header = T, sep = ",", na=-99, stringsAsFactors = FALSE)

# deleting first row because it is unecessary 
data <- data[-c(1),]

# retyping data so empty cases are read as NA
data <- data %>% retype()

# Creating Preview variable. 1 = Finished survey, 0 = Not finished survey
data <- mutate(data, Preview = ifelse(V10 == 1, 1, 0))

# Filtering only finished surveys
data <- data %>% filter(Preview == 1)

# Prepping by setting NA to 0 for Race variables 
data$Race_1[is.na(data$Race_1)] <- 0
data$Race_2[is.na(data$Race_2)] <- 0
data$Race_3[is.na(data$Race_3)] <- 0
data$Race_4[is.na(data$Race_4)] <- 0
data$Race_5[is.na(data$Race_5)] <- 0
data$Race_6[is.na(data$Race_6)] <- 0
data$Race_7[is.na(data$Race_7)] <- 0

# Creating Race variable 
data <- data %>% mutate(Race = case_when(
                        Race_1 == 1 & Race_2 == 0 & Race_3 == 0 & Race_4 == 0 & Race_5 == 0 & Race_6 == 0 & Race_7 == 0 ~ "1",
                        Race_1 == 0 & Race_2 == 1 & Race_3 == 0 & Race_4 == 0 & Race_5 == 0 & Race_6 == 0 & Race_7 == 0 ~ "2",
                        Race_1 == 0 & Race_2 == 0 & Race_3 == 1 & Race_4 == 0 & Race_5 == 0 & Race_6 == 0 & Race_7 == 0 ~ "3",
                        Race_1 == 0 & Race_2 == 0 & Race_3 == 0 & Race_4 == 1 & Race_5 == 0 & Race_6 == 0 & Race_7 == 0 ~ "4",
                        Race_1 == 0 & Race_2 == 0 & Race_3 == 0 & Race_4 == 0 & Race_5 == 1 & Race_6 == 0 & Race_7 == 0 ~ "5",
                        Race_1 == 0 & Race_2 == 0 & Race_3 == 0 & Race_4 == 0 & Race_5 == 0 & Race_6 == 1 & Race_7 == 0 ~ "6",
                        Race_1 == 0 & Race_2 == 0 & Race_3 == 0 & Race_4 == 0 & Race_5 == 0 & Race_6 == 0 & Race_7 == 1 ~ "7"))

# Filtering by race 
data <- data %>% filter(Race == 3)

# Saved tidy version of data 
# write.csv(data, 'TidyData.csv')

```
Invsibility Composite
```{r invisibility_composite}
# Higher values = greater invisibility

in.raw <- data %>%
  dplyr::select(NtvInvisibility_1, 
                NtvInvisibility_2, 
                NtvInvisibility_3,
                NtvInvisibility_4,
                NtvInvisibility_5,
                NtvInvisibility_6,
                Invisibility1_13,
                Invisibility1_14,
                Invisibility1_15,
                Invisibility1_16,
                Invisibility1_17,
                Invisibility1_18)

in.key <- c(1, -1, 1, 1, 1, 
            1, 1, -1, 1, 1, 
            1, 1)

in.r <-
  reverse.code(in.key,
               in.raw,
               mini = 1,
               maxi = 7)

invisibility.df <- as.data.frame(in.r)

#Item Analysis:
# psych::alpha(in.df, check.keys = TRUE)

Invisibility <-
  multicon::composite(invisibility.df,
  rel = TRUE,
  nomiss = 0.6)
```

Invisibility Factor loadings
```{r}
corMat <- cor(invisibility.df, use = "pairwise.complete.obs")
solutionX <- fa(r = corMat, nfactors = 3, rotate = "varimax", fm = "pa")
solutionX
```

Creating New Factors
```{r}
Fac1.raw <- data %>% select(
  NtvInvisibility_4,
  NtvInvisibility_5,
  NtvInvisibility_6,
  Invisibility1_15,
  Invisibility1_16,
  Invisibility1_17,
  Invisibility1_18
)

Fac1 <- multicon::composite(Fac1.raw,
  rel = TRUE,
  nomiss = 0.6)

Fac2.raw <- data %>% select(
  NtvInvisibility_1,
  NtvInvisibility_2,
  NtvInvisibility_3
)

Fac2.key <- c(1, -1, 1)

Fac2.r <-
  reverse.code(Fac2.key,
               Fac2.raw,
               mini = 1,
               maxi = 7)

Fac2 <- multicon::composite(Fac2.raw,
  rel = TRUE,
  nomiss = 0.6)

Fac2_sans2 <- data %>% select(
  NtvInvisibility_1,
  NtvInvisibility_3
)

Fac2_sans2 <- multicon::composite(Fac2_sans2,
  rel = TRUE,
  nomiss = 0.6)

Fac3.raw <- data %>% select(
  Invisibility1_13,
  Invisibility1_14
)

Fac3.key <- c(1, -1)

Fac3.r <-
  reverse.code(Fac3.key,
               Fac3.raw,
               mini = 1,
               maxi = 7)

Fac3 <- multicon::composite(Fac3.r,
  rel = TRUE,
  nomiss = 0.6)

cor(Support, Fac2)
cor(Support, Fac2_sans2)
```

Racism Minimization Composite
```{r race_mini_composite}
racemini.raw <- data %>%
  dplyr::select(
    RacismMini_1:RacismMini_10)

racemini.key <- c(1, -1, 1, -1, -1,
                  -1, -1, 1, 1, 1)

racemini.r <- reverse.code(racemini.key,
                           racemini.raw,
                           mini = 1,
                           maxi = 7)

racemini.df <- as.data.frame(racemini.r)

RaceMini <-
  multicon::composite(racemini.df, rel = TRUE, nomiss = 0.6)

```

Victim Blaming Composite
```{r vic_blame_composite}
vicblame.raw <- data %>%
  dplyr::select(
    AB_Activists,
    AB_SexWork,
    AB_Rez,
    AB_Runaways,
    AB_Drug,
    AB_Criminal
    )

#Took out the key and reverse coding since the direction did not change for any of these values. 

vicblame.df <- as.data.frame(vicblame.raw)

VictimBlaming <- multicon::composite(vicblame.df, rel=TRUE, nomiss = 0.6)
```

Structural Forces Composite
```{r structural_forces_composite}
structuralforces.raw <- data %>%
  dplyr::select(
    AB_NonNative.pers,
    AB_Citizens,
    AB_MaleWorker,
    AB_TribalPolice,
    AB_Laws,
    AB_Society
    )

structuralforces.df <- as.data.frame(structuralforces.raw)

StructuralForces <- multicon::composite(structuralforces.df, rel = TRUE, nomiss=0.6)

```

Support Composite
```{r support_composite}
# Higher values = more support
sup <- data %>%
  dplyr::select(Sup_Hash:Sup_Training)

sup.df <- as.data.frame(sup)

# psych::alpha(sup.df, check.keys = TRUE)

Support <-
  multicon::composite(sup.df,
  rel = TRUE,
  nomiss = 0.6)
```

# Mediation Analysis

## Invisibility to Racism Minimization Mediation Model
```{r}
var <- data.frame(Support, VictimBlaming, StructuralForces, Invisibility, RaceMini, Fac1, Fac2, Fac2_sans2)

rm.in.multipleMediation <- '
    RaceMini ~ Invisibility
    VictimBlaming ~ Invisibility
    StructuralForces ~ Invisibility
    Support ~ Invisibility
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * RaceMini
    VictimBlaming ~ a1 * RaceMini
    StructuralForces ~ a2 * RaceMini
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

rm.in.fit <- sem(model = rm.in.multipleMediation, data = var)
summary(rm.in.fit) 


```

## Factor 1 Model
```{r}

fac1.multipleMediation <- '
    RaceMini ~ Fac1
    VictimBlaming ~ Fac1
    StructuralForces ~ Fac1
    Support ~ Fac1
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * RaceMini
    VictimBlaming ~ a1 * RaceMini
    StructuralForces ~ a2 * RaceMini
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

fac1.fit <- sem(model = fac1.multipleMediation, data = var)
summary(fac1.fit) 
```

## Factor 2 Model
```{r}

fac2.multipleMediation <- '
    RaceMini ~ Fac2
    VictimBlaming ~ Fac2
    StructuralForces ~ Fac2
    Support ~ Fac2
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * RaceMini
    VictimBlaming ~ a1 * RaceMini
    StructuralForces ~ a2 * RaceMini
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

fac2.fit <- sem(model = fac2.multipleMediation, data = var)
summary(fac2.fit) 

```

# Factor 2 model wihout reverse scored item
```{r}

fac2.sans2.multipleMediation <- '
    RaceMini ~ Fac2_sans2
    VictimBlaming ~ Fac2_sans2
    StructuralForces ~ Fac2_sans2
    Support ~ Fac2_sans2
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * RaceMini
    VictimBlaming ~ a1 * RaceMini
    StructuralForces ~ a2 * RaceMini
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

fac2.sans2.fit <- sem(model = fac2.sans2.multipleMediation, data = var)
summary(fac2.sans2.fit) 

```


## Smaller Invisibility Mediation Model with Factor 2 
```{r Smaller mediation model}

in.multipleMediation <- '
    Support ~ b1 * VictimBlaming + b2 * StructuralForces + c * Fac2_sans2
    VictimBlaming ~ a1 * Fac2_sans2
    StructuralForces ~ a2 * Fac2_sans2
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    VictimBlaming ~~ StructuralForces 
'

in.fit <- sem(model = in.multipleMediation, data = var)
summary(in.fit)    

```

