---
title: "MMIWG_1"
author: "Jamie Yellowtail"
date: "8/13/2019"
output: word_document
editor_options: 
  chunk_output_type: console
---
```{r}
library(rio)
library(tidyverse)
library(broom)
library(lmSupport)
library(olsrr)
library(psych)
library(readr)
library(dplyr)
library(ggplot2)
install.packages("GGally")
library(GGally)
options(scipen = 999)

#install.packages("devtools")
#devtools::install_github("ropensci/qualtRics")

library(qualtRics)
MMIWG1 <- readSurvey("MMIWG_1.csv")

View(MMIWG1)
#str(MMIWG1)



MMIWG1 <- MMIWG1 %>% 
  mutate(Gender = factor(Gender, 
                        labels = c("Male", "Female")),
         BorninUS = factor(BorninUS,
                        labels = c("No", "Yes")),
         SES = factor(SES,
                      labels = c("High School", "Associates/Technical Degree", "BA/BS", "MA/MS", "Doctorate")),
         Citizen = factor(Citizen,
                          labels = c("No", "Yes")),
         LibCon = factor(LibCon,
                         labels = c("Extremely Conservative", "Conservative", "Somewhat Conservative", "Moderate", "Somewhat Liberal", "Liberal", "Extremely Liberal")),
         NewsSource = factor(NewsSource,
                             labels = c("NatTV", "LocalTV", "SocialMedia", "Radio/Podcast", "OnlineBlog", "NatNewspaper", "LocalNewspaper", "PublishedResearch", "WordofMouth", "Unsure")))

MMIWG1 <- MMIWG1 %>% 
  rename(Mauna_Kea = Movements_16)

```

#Knowledge of Social Movements
```{r}
#MeToo
summary(MMIWG1$MeToo)
describe(MMIWG1$MeToo)

#March for our Lives
summary(MMIWG1$March4lives)
describe(MMIWG1$March4lives)

#Black Lives Matter
summary(MMIWG1$BLM)
describe(MMIWG1$BLM)

#All Lives Matter
summary(MMIWG1$AllLives)
describe(MMIWG1$AllLives)

#NoDAPL
summary(MMIWG1$NODAPL)
describe(MMIWG1$NODAPL)

#Native Lives Matter
summary(MMIWG1$NativeLives)
describe(MMIWG1$NativeLives)

#Zero Hour
summary(MMIWG1$ZeroHour)
describe(MMIWG1$ZeroHour)

#Blue Lives Matter
summary(MMIWG1$BlueLives)
describe(MMIWG1$BlueLives)

#Men's Rights
summary(MMIWG1$MenRights)
describe(MMIWG1$MenRights)

#White Nationalist
summary(MMIWG1$WhiteNationa)
describe(MMIWG1$WhiteNationa)

#Straight Pride
summary(MMIWG1$StraightPride)
describe(MMIWG1$StraightPride)

#LGBTQ+ Pride
summary(MMIWG1$LGBTQ)
describe(MMIWG1$LGBTQ)

#Right to Life
summary(MMIWG1$Right2Life)
describe(MMIWG1$Right2Life)

#Missing and Murdered Indigenous Women and Girls
summary(MMIWG1$MMIWG)
describe(MMIWG1$MMIWG)

#TimesUp
summary(MMIWG1$Timesup)
describe(MMIWG1$Timesup)

#MaunaKea     
summary(MMIWG1$Mauna_Kea)
describe(MMIWG1$Mauna_Kea)

#Native Social Movements
MMIWG1<-mutate(MMIWG1, NatSM = rowMeans(MMIWG1[,c("MMIWG", "NativeLives", "NODAPL","Mauna_Kea")]))
summary(MMIWG1$NatSM)
describe(MMIWG1$NatSM)

#Non-Native Social Movements
MMIWG1<-mutate(MMIWG1, NonNatSM = rowMeans(MMIWG1[,c("MeToo", "March4lives", "BLM","AllLives", "ZeroHour", "BlueLives", "MenRights", "WhiteNationa", "StraightPride", "LGBTQ", "Right2Life", "Timesup")]))
summary(MMIWG1$NonNatSM)
describe(MMIWG1$NonNatSM)


```
#Attitudes and Beliefs About Contributing Factors to MMIWG
```{r}
# higher signifies more negative attitudes
MMIWG1 <- MMIWG1 %>% 
  rename(`AB_NonNative_pers` = `AB_NonNative pers`)

att <- MMIWG1 %>%
  dplyr::select(
    AB_Activists,
    AB_SexWork,
    AB_NonNative_pers,
    AB_Rez,
    AB_Citizens,
    AB_Runaways,
    AB_Drug,
    AB_MaleWorker,
    AB_Criminal,
    AB_TwoParent,
    AB_TribalPolice,
    AB_Poverty,
    AB_NativeComm,
    AB_Society,
    AB_Abusive,
    AB_Laws
    )

att.key = c(1, 1, -1, 1, -1, 1, 1, -1,
               1, 1, -1, 1, 1, 1, 1, -1) #Reverse Scoring

att.r <-
  reverse.code(att.key,
               att,
               mini = 1,
               maxi = 7)

att.df <- as.data.frame(att.r)

att.df[is.na(att.df)] <- 0

psych::alpha(att.df, check.keys = TRUE)

att.comp <- multicon::composite(att.df, rel=TRUE, nomiss = 0)

MMIWG1<-mutate(MMIWG1, Att_and_Belief_Score = rowMeans(MMIWG1[,c("AB_Activists", "AB_SexWork", "AB_NonNative_pers","AB_Rez", "AB_Citizens", "AB_Runaways", "AB_Drug", "AB_MaleWorker", "AB_Criminal", "AB_TwoParent", "AB_TribalPolice", "AB_Poverty", "AB_NativeComm", "AB_Society", "AB_Abusive", "AB_Laws")]))
summary(MMIWG1$Att_and_Belief_Score)
describe(MMIWG1$Att_and_Belief_Score)

```
#If Familiar
```{r}
#National Television
describe(MMIWG1$`IF FAMILIAR_1`)
summary(MMIWG1$`IF FAMILIAR_1`)
#Local Television
describe(MMIWG1$`IF FAMILIAR_2`)
summary(MMIWG1$`IF FAMILIAR_2`)
#Social Media
describe(MMIWG1$`IF FAMILIAR_3`)
summary(MMIWG1$`IF FAMILIAR_3`)
#Word of Mouth
describe(MMIWG1$`IF FAMILIAR_6`)
summary(MMIWG1$`IF FAMILIAR_6`)
#Radio/Podcast
describe(MMIWG1$`IF FAMILIAR_7`)
summary(MMIWG1$`IF FAMILIAR_7`)
#Online Blogs
describe(MMIWG1$`IF FAMILIAR_8`)
summary(MMIWG1$`IF FAMILIAR_8`)
#National Newspapers
describe(MMIWG1$`IF FAMILIAR_10`)
summary(MMIWG1$`IF FAMILIAR_10`)
#Unsure
describe(MMIWG1$`IF FAMILIAR_11`)
summary(MMIWG1$`IF FAMILIAR_11`)
#Published Research Report
describe(MMIWG1$`IF FAMILIAR_13`)
summary(MMIWG1$`IF FAMILIAR_13`)
#Local Newspaper
describe(MMIWG1$`IF FAMILIAR_14`)
summary(MMIWG1$`IF FAMILIAR_14`)

```
#Primary Source
```{r}
MMIWG1 <- MMIWG1 %>% 
  mutate(SourceOnMMIWG = factor(SourceOnMMIWG, 
                        labels = c("NationalTV", "LocalTV", "SocialMedia", "WordofMouth", "Radio/Podcast", "OnlineBlogs", "NationalNewspaper", "PublishedResearch", "Unsure", "LocalNewspaper", "NotListed")))
summary(MMIWG1$SourceOnMMIWG)


```
#Support for MMIWG
```{r}
MMIWG1<-mutate(MMIWG1, Support_MMIWG = rowMeans(MMIWG1[,c("Sup_Hash", "Sup_Letter", "Sup_Donate","Sup_Authority", "Sup_Prosecute", "Sup_Access", "Sup_Training")]))
summary(MMIWG1$Support_MMIWG)
describe(MMIWG1$Support_MMIWG)
```
#Responsibility
```{r}

str(MMIWG1$Res_Stopping_1)
summary(MMIWG1$Res_Stopping_1)
describe(MMIWG1$Res_Stopping_1)

#Who is responsible for STOPPING the epidemic of MMIWG?
    #State & National Government

summary(MMIWG1$Res_Stopping_1)
describe(MMIWG1$Res_Stopping_1)
    #Native American Tribes
summary(MMIWG1$Res_Stopping_2)
describe(MMIWG1$Res_Stopping_2)
    #All Americans
summary(MMIWG1$Res_Stopping_3)
describe(MMIWG1$Res_Stopping_3)
    #Parents and Families of MMIWG
summary(MMIWG1$Res_Stopping_4)
describe(MMIWG1$Res_Stopping_4)
#Who is responsible for PREVENTING individual MMIWG attacks?
    #State & National Government
summary(MMIWG1$Res_Preventing_1)
describe(MMIWG1$Res_Preventing_1)
    #Native American Tribes
summary(MMIWG1$Res_Preventing_2)
describe(MMIWG1$Res_Preventing_2)
    #All Americans
summary(MMIWG1$Res_Preventing_3)
describe(MMIWG1$Res_Preventing_3)
    #Parents and Families of MMIWG
summary(MMIWG1$Res_Preventing_4)
describe(MMIWG1$Res_Preventing_4)
#Who is responsible for bringing awareness MMIWG?
    #State & National Government
summary(MMIWG1$Res_Awareness_1)
describe(MMIWG1$Res_Awareness_1)
    #Native American Tribes
summary(MMIWG1$Res_Awareness_1)
describe(MMIWG1$Res_Awareness_1)
    #All Americans
summary(MMIWG1$Res_Awareness_1)
describe(MMIWG1$Res_Awareness_1)
    #Parents and Families of MMIWG
summary(MMIWG1$Res_Awareness_1)
describe(MMIWG1$Res_Awareness_1)

####Not sure why this is not running... variable values are numeric, but listed as chr... should be able to get descriptives.
```
#Invisibility
```{r}
MMIWG1 <- MMIWG1 %>% 
  rename(NtvInvisibility_7 = Invisibility1_13,
         NtvInvisibitity_8 = Invisibility1_14,
         NtvInvisibility_9 = Invisibility1_15,
         NtvInvisibility_10 = Invisibility1_16,
         NtvInvisibility_11 = Invisibility1_17,
         NtvInvisibility_12 = Invisibility1_18)

MMIWG1<-mutate(MMIWG1, Ntv_Invisibility = rowMeans(MMIWG1[,c("NtvInvisibility_1", "NtvInvisibility_2", "NtvInvisibility_3","NtvInvisibility_4", "NtvInvisibility_5", "NtvInvisibility_6", "Invisibility1_13", "Invisibility1_14", "Invisibility1_15", "Invisibility1_16", "Invisibility1_17", "Invisibility1_18", "IN_Violence")]))
summary(MMIWG1$Ntv_Invisibility)
describe(MMIWG1$Ntv_Invisibility)

###REVERSE CODING###
```
#Perception of Sovereignty
```{r}
MMIWG1<-mutate(MMIWG1, Percep_Sov = rowMeans(MMIWG1[,c("Sov_Rules", "Sov_Legal", "Sov_Police","Sov_Gov", "Sov_Auto", "Sov_Rely", "Sov_Jurisdiction")]))
summary(MMIWG1$Ntv_Invisibility)
describe(MMIWG1$Ntv_Invisibility)

###REVERSE CODING###
```
#Racism Minimization
```{r}
MMIWG1<-mutate(MMIWG1, RM_Score = rowMeans(MMIWG1[,c("RacismMini_1", "RacismMini_2", "RacismMini_3","RacismMini_4", "RacismMini_5", "RacismMini_6", "RacismMini_7", "RacismMini_8", "RacismMini_9", "RacismMini_10")]))
summary(MMIWG1$RM_Score)
describe(MMIWG1$RM_Score)

#REVERSE CODING###
```
#Cultural Racism
```{r}

MMIWG1<-mutate(MMIWG1, CR_Score = rowMeans(MMIWG1[,c("CulturalRacism_1", "CulturalRacism_2", "CulturalRacism_3","CulturalRacism_4", "CulturalRacism_5", "CulturalRacism_6", "CulturalRacism_7", "CulturalRacism_8", "CulturalRacism_9", "CulturalRacism_10", "CulturalRacism_11", "CulturalRacism_12","CulturalRacism_13")]))
summary(MMIWG1$CR_Score)
describe(MMIWG1$CR_Score)

###REVERSE CODING###
```
#Dehumanization- Natives
```{r}
#Responsible
summary(MMIWG1$NtvDehum_1)
describe(MMIWG1$NtvDehum_1)

#Civilized
summary(MMIWG1$NtvDehum_2)
describe(MMIWG1$NtvDehum_2)

#Moral
summary(MMIWG1$NtvDehum_3)
describe(MMIWG1$NtvDehum_3)

#Polite
summary(MMIWG1$NtvDehum_4)
describe(MMIWG1$NtvDehum_4)

#Childlike
summary(MMIWG1$NtvDehum_5)
describe(MMIWG1$NtvDehum_5)

#Rational
summary(MMIWG1$NtvDehum_6)
describe(MMIWG1$NtvDehum_6)

#Warm
summary(MMIWG1$NtvDehum_7)
describe(MMIWG1$NtvDehum_7)

#Having Agency
summary(MMIWG1$NtvDehum_8)
describe(MMIWG1$NtvDehum_8)

#Native Dehumanization Score
MMIWG1<-mutate(MMIWG1, NtvDehum_Score = rowMeans(MMIWG1[,c("NtvDehum_1", "NtvDehum_2", "NtvDehum_3","NtvDehum_4", "NtvDehum_5", "NtvDehum_6", "NtvDehum_7", "NtvDehum_8")]))
summary(MMIWG1$NtvDehum_Score)
describe(MMIWG1$NtvDehum_Score)

###REVERSE CODING###
```
#Dehumanization- Whites
```{r}
#Responsible
summary(MMIWG1$WhiteDehuman_1)
describe(MMIWG1$WhiteDehuman_1)

#Civilized
summary(MMIWG1$WhiteDehuman_2)
describe(MMIWG1$WhiteDehuman_2)

#Moral
summary(MMIWG1$WhiteDehuman_3)
describe(MMIWG1$WhiteDehuman_3)

#Polite
summary(MMIWG1$WhiteDehuman_4)
describe(MMIWG1$WhiteDehuman_4)

#Childlike
summary(MMIWG1$WhiteDehuman_5)
describe(MMIWG1$WhiteDehuman_5)

#Rational
summary(MMIWG1$WhiteDehuman_6)
describe(MMIWG1$WhiteDehuman_6)

#Warm
summary(MMIWG1$WhiteDehuman_7)
describe(MMIWG1$WhiteDehuman_7)

#Having Agency
summary(MMIWG1$WhiteDehuman_8)
describe(MMIWG1$WhiteDehuman_8)

#White Dehumanization Score
MMIWG1<-mutate(MMIWG1, WhiteDehum_Score = rowMeans(MMIWG1[,c("WhiteDehuman_1", "WhiteDehuman_2", "WhiteDehuman_3","WhiteDehuman_4", "WhiteDehuman_5", "WhiteDehuman_6", "WhiteDehuman_7", "WhiteDehuman_8")]))
summary(MMIWG1$WhiteDehum_Score)
describe(MMIWG1$WhiteDehum_Score)

###REVERSE CODING###
```
#Feelings Thermometer
```{r}
#Natives
summary(MMIWG1$NtvFeelings_31)
describe(MMIWG1$NtvFeelings_31)

#Whites
summary(MMIWG1$White_thermo_31)
describe(MMIWG1$White_thermo_31)
```
#Ambivalent Sexism
```{r}
#Hostile Sexism Score
MMIWG1<-mutate(MMIWG1, HS_Score = rowMeans(MMIWG1[,c("ASI_1", "ASI_2", "ASI_3","ASI_4", "ASI_5", "ASI_6", "ASI_7", "ASI_8", "ASI_9","ASI_10","ASI_11")]))
summary(MMIWG1$HS_Score)
describe(MMIWG1$HS_Score)
#Benevolent Sexism Score
MMIWG1<-mutate(MMIWG1, BS_Score = rowMeans(MMIWG1[,c("ASI_12", "ASI_13", "ASI_14","ASI_15", "ASI_16", "ASI_17", "ASI_18", "ASI_19", "ASI_20","ASI_21","ASI_22")]))
summary(MMIWG1$BS_Score)
describe(MMIWG1$BS_Score)
#Overall ASI Score
MMIWG1<-mutate(MMIWG1, ASI_Score = rowMeans(MMIWG1[,c("HS_Score","BS_Score")]))
summary(MMIWG1$ASI_Score)
describe(MMIWG1$ASI_Score)

###REVERSE CODING###
```
#Race
```{r}
#Asian/Pacific Islander=16
#Black/African American=42
#White/Caucasian=205
#Hispanic/Latino=27
#MiddleE Eastern= 
#Native American=10
#Another racial/ethnic background=3
#Text= Filipino, Mixed, mixed

```
#Gender 
```{r}
summary(MMIWG1$Gender)
```
#Age
```{r}
str(MMIWG1$Age)
describe(MMIWG1$Age)
```
#Born in the US
```{r}
summary(MMIWG1$BorninUS)
```
#SES
```{r}
summary(MMIWG1$SES)
```
#Citizen
```{r}
summary(MMIWG1$Citizen)
```
#Liberal/Conservative
```{r}
summary(MMIWG1$LibCon)
```
#News Source
```{r}
summary(MMIWG1$NewsSource)
```