---
title: "MMIWG"
author: "Julisa Lopez"
date: "10/1/2019"
output:
  html_document:
    toc: True
    toc_depth: 5
    toc_float:
      collapsed: False
    number_sections: True
    code_folding: hide
editor_options: 
  chunk_output_type: console
---

Necessary Packages
```{r}

library(psych) # For reverse coding variables, reading data files and item analysis
library(multicon) # For creating composites
library(tidyverse)
#install.packages("haven")
library(haven)
#install.packages("labelled")
library(labelled)
#install.packages("nFactors")
library(nFactors) # Determines how many factors to extract
library(dplyr) #clean up data
#install.packages("corrplot")
library(corrplot) # For correlation matrix
library(GGally)
#install.packages("Rmisc") #Multiplot
library(Rmisc)
library(survey) # correlation plot with significance
library(xtable) # creates html tables 
library(htmltools)
library(htmlTable)

#install.packages(c("psych", "multicon", "tidyverse", "haven", "labelled", "nFactors", "dplyr", "corrplot", "GGally", "Rmisc", "survey", "xtable", "htmltools", "htmlTable"))

library(backports)

```


Prepping Data File
```{r Read Data File}

data <- read_spss("C:/Users/Julisa/Desktop/MMIWG.sav")

data <- data %>%
  dplyr::rename(Mauna_Kea = Movements_16)

data <- data %>% dplyr::filter(Race == 3)



```

Corstars function to create correlation matrix with astrix
```{r}
corstars <-function(x, method=c("pearson", "spearman"), removeTriangle=c("upper", "lower"),
                     result=c("none", "html", "latex")){
    #Compute correlation matrix
    require(Hmisc)
    x <- as.matrix(x)
    correlation_matrix<-rcorr(x, type=method[1])
    R <- correlation_matrix$r # Matrix of correlation coeficients
    p <- correlation_matrix$P # Matrix of p-value 
    
    ## Define notions for significance levels; spacing is important.
    mystars <- ifelse(p < .0001, "****", ifelse(p < .001, "*** ", ifelse(p < .01, "**  ", ifelse(p < .05, "*   ", "    "))))
    
    ## trunctuate the correlation matrix to two decimal
    R <- format(round(cbind(rep(-1.11, ncol(x)), R), 2))[,-1]
    
    ## build a new matrix that includes the correlations with their apropriate stars
    Rnew <- matrix(paste(R, mystars, sep=""), ncol=ncol(x))
    diag(Rnew) <- paste(diag(R), " ", sep="")
    rownames(Rnew) <- colnames(x)
    colnames(Rnew) <- paste(colnames(x), "", sep="")
    
    ## remove upper triangle of correlation matrix
    if(removeTriangle[1]=="upper"){
      Rnew <- as.matrix(Rnew)
      Rnew[upper.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove lower triangle of correlation matrix
    else if(removeTriangle[1]=="lower"){
      Rnew <- as.matrix(Rnew)
      Rnew[lower.tri(Rnew, diag = TRUE)] <- ""
      Rnew <- as.data.frame(Rnew)
    }
    
    ## remove last column and return the correlation matrix
    Rnew <- cbind(Rnew[1:length(Rnew)-1])
    if (result[1]=="none") return(Rnew)
    else{
      if(result[1]=="html") print(xtable(Rnew), type="html")
      else print(xtable(Rnew), type="latex") 
    }
} 
```

# Demographics

## Race
```{r}
#table(data$Race)
```

## Gender
Gender: Male- 166; Females-114; N/A-20
No entries: Transgender man, Transgender woman, Non-binary, Genderqueer
```{r}
#table(data$Gender)
```

## SES - highest level of education
HS Diploma = 73, AA = 45, BA/BS = 132, MA/MS = 26, Doctorate = 5

```{r}
# table(data$SES)
```

## Born in US
Born in the US: Yes- 269; No-12; N/A- 19

```{r}
# table(data$BorninUS)
```

## Citizen
No-3 Yes-9; N/A- 288
```{r}
# table(data$Citizen)
```

## Age
```{r}

summary(data$Age.r)

Age <- as.data.frame(data$Age.r)

```

## Liberal/Conservative
```{r}

summary(data$LibCon)

LibCon <- as.data.frame(data$LibCon)


#Liberal/Conservative: Extremely Conservative:20; Conservative:26; Somewhat Conservative:21; Moderate:69; Somewhat Liberal:42; Liberal:51; Extremely Liberal: 49; NA: 22
```

## News Source
Primary News Source: National TV: 76; Local TV: 20; Social Media: 97; Radio/Podcast: 13; Online Blog: 23; National Newspaper: 33; Local Newspaper: 7; Published Research Report: 4; Word of Mouth: 6; Unsure: 2; N/A: 19
```{r}

# (primnews <- (table(data$NewsSource)))


```


# Knowledge of Social Movements

Knowledge about Metoo
```{r}
# Knowledge about MeToo 

summary(data$MeToo)

table(data$MMIWG)

MeToo <- as.data.frame(data$MeToo)

# Knowledge about MMIWG


```

Knowledge about MMIWG
```{r}
summary(data$MMIWG)

MMIWG <- as.data.frame(data$MMIWG)

```

# Attitudes and Beliefs (3 Factors)

1. Victim Blaming
+ MMIWG are not as big of a problem as activists would like people to think.
+ MMIWG were involved in sex work.
+ MMIWG only takes place on the reservation.
+ MMIWG under 18 were runaways.
+ MMIWG were using drugs and/or alcohol.
+ MMIWG were involved in criminal activity.

```{r}
#Higher = More victim blame

vicblame.raw <- data %>%
  dplyr::select(
    AB_Activists,
    AB_SexWork,
    AB_Rez,
    AB_Runaways,
    AB_Drug,
    AB_Criminal
    )

vicblame.key <- c(1, 1, 1, 1, 1, 1)

vicblame.r <- reverse.code(vicblame.key,
                           vicblame.raw,
                           mini = 1,
                           maxi = 7)

vicblame.df <- as.data.frame(vicblame.r)

VictimBlaming <- multicon::composite(vicblame.df, rel=TRUE, nomiss = 0.6)
```


2. Institution level and outside factors
+ MMIWG are a result of violence perpetrated by non-Natives.
+ Ending the MMIWG crisis is the responsibility of all U.S. citizens.
+ Non-native male workers that live near reservations contribute to the high rates of  MMIWG.
+ Tribal police forces do not have the resources to prevent Native women from being murdered and going missing.
+ Policies and laws that make it difficult to prosecute Non-native offenders contribute to the epidemic of MMIWG.
+ Native women are murdered and go missing because U.S. society does not value Native women.

```{r}
# Higher = Takes into account external factors

externfactors.raw <- data %>%
  dplyr::select(
    AB_NonNative_pers,
    AB_Citizens,
    AB_MaleWorker,
    AB_TribalPolice,
    AB_Laws,
    AB_Society
    )

externfactors.key <- c(1, 1, 1, 1, 1, -1)

externfactors.r <- reverse.code(externfactors.key,
                                externfactors.raw,
                                mini=1,
                                maxi=7)

externfactors.df <- as.data.frame(externfactors.r)

ExternalFactors <- multicon::composite(externfactors.df, rel = TRUE, nomiss=0.6)
```


3. Community Blame
+ The lack of two parent homes in tribal communities puts Native American girls at risk of going missing.
+ MMIWG are the result of poverty within Native communities.
+ Native women are murdered and go missing because Native communities do not value Native women.
+ MMIWG under 18 come from abusive homes.

```{r}
# Higher = more community blame, more negative attitudes

commblame.raw <- data %>%
  dplyr::select(
    AB_TwoParent,
    AB_Poverty,
    AB_NativeComm,
    AB_Abusive
    )

commblame.key <- c(1, 1, 1, 1)

commblame.r <-
  reverse.code(commblame.key,
               commblame.raw,
               mini = 1,
               maxi = 7)

commblame.df <- as.data.frame(commblame.r)


CommunityBlame <- multicon::composite(commblame.df, rel = TRUE, nomiss = 0.6)

```

# Support for ending MMIWG (5 point)
```{r}
# Higher values = more support

sup <- data %>%
  dplyr::select(Sup_Hash,
                Sup_Letter,
                Sup_Donate,
                Sup_Authority,
                Sup_Prosecute,
                Sup_Access,
                Sup_Training
                )

sup.df <- as.data.frame(sup)

# psych::alpha(sup.df, check.keys = TRUE)

Support <-
  multicon::composite(sup.df,
  rel = TRUE,
  nomiss = 0.6)

```

# Responsibility

## Who is responsible for stopping the epidemic of MMIWG?
US Government, Tribal Government, US Citizens, Parents and Families of victims
```{r}

summary(data$Res_Stopping_1)
summary(data$Res_Stopping_2)
summary(data$Res_Stopping_3)
summary(data$Res_Stopping_4)

```

## Who is responsible for preventing individual MMIWG attacks?
US Government, Tribal Government, US Citizens, Parents and Families of victims
```{r}
summary(data$Res_Preventing_1)
summary(data$Res_Preventing_2)
summary(data$Res_Preventing_3)
summary(data$Res_Preventing_4)
```

## Who is responsible for bringing awareness to MMIWG?
US Government, Tribal Government, US Citizens, Parents and Families of victims
```{r}

summary(data$Res_Awareness_1)  
summary(data$Res_Awareness_2)
summary(data$Res_Awareness_3)
summary(data$Res_Awareness_4)

```

# Invisibility

Overall Invisibility Scale
```{r}
# Higher values = greater invisibility

data.in <- data %>%
  dplyr::rename(NtvInvisibility_7 = Invisibility1_13,
         NtvInvisibility_8 = Invisibility1_14,
         NtvInvisibility_9 = Invisibility1_15,
         NtvInvisibility_10 = Invisibility1_16,
         NtvInvisibility_11 = Invisibility1_17,
         NtvInvisibility_12 = Invisibility1_18,
         NtvInvisibility_1 = NtvInvisibility_1,
         NtvInvisibility_2 = NtvInvisibility_2,
         NtvInvisibility_3 = NtvInvisibility_3,
         NtvInvisibility_4 = NtvInvisibility_4,
         NtvInvisibility_5 = NtvInvisibility_5,
         NtvInvisibility_6 = NtvInvisibility_6)

in.raw <- data.in %>%
  dplyr::select(
    NtvInvisibility_1,
    NtvInvisibility_2,
    NtvInvisibility_3,
    NtvInvisibility_4,
    NtvInvisibility_5,
    NtvInvisibility_6,
    NtvInvisibility_7,
    NtvInvisibility_8,
    NtvInvisibility_9,
    NtvInvisibility_10,
    NtvInvisibility_11,
    NtvInvisibility_12
    )

in.key <- c(1, -1, 1, 1,
           1, 1, 1, -1,
           1, 1, 1, 1)

in.r <-
  reverse.code(in.key,
               in.raw,
               mini = 1,
               maxi = 7)

in.df <- as.data.frame(in.r)

# Item analysis

# psych::alpha(in.df, check.keys = TRUE)

Invisibility <-
  multicon::composite(in.df,
  rel = TRUE,
  nomiss = 0.6)

```

1. Factor 1
+ I rarely think about Native/Indigenous Americans in contemporary society.
+ When I think about poverty, Native/Indigenous Americans do not come to mind.
+ When I think about groups that experience racism and discrimination Native/Indigenous Americans do not come to mind.
+ When I think about successful Americans, Native/Indigenous do not come to mind.
+ When I think about actors and actresses, Native/Indigenous Americans do not come to mind.
+ When I think about healthy families, Native/Indigenous Americans do not come to mind.
+ When I think about health disparities, Native/Indigenous Americans come to mind.

```{r}
# Factor 1 - higher = more invisible

in.fac1.raw <- data.in %>%
  dplyr::select(
    NtvInvisibility_6,
    NtvInvisibility_7,
    NtvInvisibility_8,
    NtvInvisibility_9,
    NtvInvisibility_10,
    NtvInvisibility_11,
    NtvInvisibility_12
    )

in.fac1.key <- c(1, 1, -1, 1,
           1, 1, 1)

in.fac1.r <-
  reverse.code(in.fac1.key,
               in.fac1.raw,
               mini = 1,
               maxi = 7)

in.fac1.df <- as.data.frame(in.fac1.r)

# Item analysis

# psych::alpha(in.fac1.df, check.keys = TRUE)

Invisibility1 <-
  multicon::composite(in.fac1.df,
  rel = TRUE,
  nomiss = 0.6)
```


2. Factor 2
+ Native/Indigenous Americans are invisible in contemporary society.
+ I rarely hear about Native/Indigenous Americans in contemporary society.

```{r}
#Factor 2 - higher = more invisible

in.fac2.raw <- data.in %>%
  dplyr::select(
    NtvInvisibility_1,
    NtvInvisibility_2,
    NtvInvisibility_3)

in.fac2.key <- c(1, -1, 1)

in.fac2.r <-
  reverse.code(in.fac2.key,
               in.fac2.raw,
               mini = 1,
               maxi = 7)

in.fac2.df <- as.data.frame(in.fac2.r)

# Item analysis

# psych::alpha(in.fac2.df, check.keys = TRUE)

Invisibility2 <-
  multicon::composite(in.fac2.df,
  rel = TRUE,
  nomiss = 0.6)
```


3. Factor 3
+ There are hardly any Native/Indigenous Americans left in U.S. society.
+ In contemporary society, there are not any real  Native/Indigenous Americans.
+ There is a significant number of Native/Indigenous Americans who live in U.S. society today.

```{r}

in.fac3.raw <- data.in %>%
  dplyr::select(
    NtvInvisibility_4,
    NtvInvisibility_5
    )

in.fac3.key <- c(1, 1)

in.fac3.r <-
  reverse.code(in.fac3.key,
               in.fac3.raw,
               mini = 1,
               maxi = 7)

in.fac3.df <- as.data.frame(in.fac3.r)

# Item analysis

# psych::alpha(in.fac3.df, check.keys = TRUE)

Invisibility3 <-
  multicon::composite(in.fac3.df,
  rel = TRUE,
  nomiss = 0.6)
```

When I think about violence against women, Native women do not come to mind 
```{r}
# Higher = more invisible
summary(data$IN_Violence)
Violence <- as.data.frame(data$IN_Violence)

```


# Knowledge about Sovereignty

* Sovereignty Items
  + Native American tribes create and enforce their own rules, policies, and laws on reservations.
  + Native American tribes manage their own police forces.
  + Native American tribes determine the nature/structure of their own government without interference from U.S. or state governments.
  + Native American tribes are self-governing, autonomous nations within the United States.
  + Native American tribes do not have control over their own judicial and legal systems.
  + Native American tribal police do not have jurisdiction over all people who reside on or are located on their reservation.
  + Native Americans tribes rely on the U.S. government to function as a nation.
```{r}
# Higher values = more knowledge about sovereignty

sov.raw <- data %>%
  dplyr::select(
    Sov_Rules,
    Sov_Legal,
    Sov_Police,
    Sov_Gov,
    Sov_Auto,
    Sov_Rely,
    Sov_Jurisdiction)

sov.key <- c(1, -1, 1, 1,
             1, -1, -1)

sov.r <- reverse.code(sov.key,
                      sov.raw,
                      mini = 1,
                      maxi = 7)

sov.df <- as.data.frame(sov.r)

# psych::alpha(sov.df, check.keys = TRUE)

Sovereignty <-
  multicon::composite(sov.df,
  rel = TRUE,
  nomiss = 0.6)

```

# Racism Minimization
```{r}
# Higher values = Greater denial of racism

racemini.raw <- data %>%
  dplyr::select(
    RacismMini_1,
    RacismMini_2,
    RacismMini_3,
    RacismMini_4,
    RacismMini_5,
    RacismMini_6,
    RacismMini_7,
    RacismMini_8,
    RacismMini_9,
    RacismMini_10
    )

racemini.key <- c(1, -1, 1, -1, -1,
                  -1, -1, 1, 1, 1)

racemini.r <- reverse.code(racemini.key,
                           racemini.raw,
                           mini = 1,
                           maxi = 7)

racemini.df <- as.data.frame(racemini.r)

RaceMini <-
  multicon::composite(racemini.df, rel = TRUE, nomiss = 0.6)

# psych::alpha(racemini.df, check.keys = TRUE)

```

# Cultural Racism
```{r}
# Higher values = More cultural racism

culturalracism.raw <- data %>%
  dplyr::select(
    CulturalRacism_1,
    CulturalRacism_2,
    CulturalRacism_3,
    CulturalRacism_4,
    CulturalRacism_5,
    CulturalRacism_6,
    CulturalRacism_7,
    CulturalRacism_8,
    CulturalRacism_9,
    CulturalRacism_10,
    CulturalRacism_11,
    CulturalRacism_12,
    CulturalRacism_13
    )

culrac.key <- c(1, 1, 1, 1, -1,
                -1, 1, 1, 1, 1,
                1, 1, 1)

culturalracism.r <- reverse.code(culrac.key,
                                 culturalracism.raw,
                                 mini = 1,
                                 maxi = 7)

culturalracism.df <- as.data.frame(culturalracism.r)

# psych::alpha(culturalracism.df, check.keys = TRUE)

CulturalRacism <-
  multicon::composite(culturalracism.df,
  rel = TRUE,
  nomiss = 0.6)
```

# Native Dehumanization
```{r}
# Higher values = greater dehumanization

ntvdehum.raw <- data %>%
  dplyr::select(NtvDehum_1,
                NtvDehum_2,
                NtvDehum_3,
                NtvDehum_4,
                NtvDehum_5,
                NtvDehum_6,
                NtvDehum_7,
                NtvDehum_8)

ntvdehum.key <- c(1, 1, 1, 1, -1,
                1, 1, 1)

ntvdehum.r <- reverse.code(ntvdehum.key,
                                 ntvdehum.raw,
                                 mini = 0,
                                 maxi = 100)

ntvdehum.df <- as.data.frame(ntvdehum.r)

# psych::alpha(ntvdehum.df, check.keys = TRUE)

NtvDehuman <-
  multicon::composite(ntvdehum.df,
  rel = TRUE,
  nomiss = 0.6)
```

# White Dehumanization
```{r}
# Higher values = More dehumanization

whitedehum.raw <- data %>%
  dplyr::select(
    WhiteDehuman_1,
    WhiteDehuman_2,
    WhiteDehuman_3,
    WhiteDehuman_4,
    WhiteDehuman_5,
    WhiteDehuman_6,
    WhiteDehuman_7,
    WhiteDehuman_8
    )
whitedehum.key <- c(1, 1, 1, 1, -1,
                1, 1, 1)

whitedehum.r <- reverse.code(whitedehum.key,
                                 whitedehum.raw,
                                 mini = 0,
                                 maxi = 100)

whitedehum.df <- as.data.frame(whitedehum.r)

WhiteDehuman <-
  multicon::composite(whitedehum.df,
  rel = TRUE,
  nomiss = 0.6)

# psych::alpha(whitedehum.df)
```

# Native Feelings thermometer
```{r}

summary(data$NtvFeelings_31)

Ntvfeeling <- as.data.frame(data$NtvFeelings_31)

```

# White Feelings Thermometer
```{r}

summary(data$White_thermo_31)

Whitefeeling <- as.data.frame(data$White_thermo_31) 

```

# ASI
```{r}
# Higher values = more sexism

asi.raw <- data %>%
  dplyr::select(
    ASI_1,
    ASI_2,
    ASI_3,
    ASI_4,
    ASI_5,
    ASI_6,
    ASI_7,
    ASI_8,
    ASI_9,
    ASI_10,
    ASI_11,
    ASI_12,
    ASI_13,
    ASI_14,
    ASI_15,
    ASI_16,
    ASI_17,
    ASI_18,
    ASI_19,
    ASI_20,
    ASI_21,
    ASI_22
    )

asi.key <- c(1, 1, 1, 1, 1,
             -1, -1, 1, -1, 1,
             1, 1, 1, 1, -1,
             1, 1, 1, 1, -1,
             1, -1)

asi.r <- reverse.code(asi.key,
                      asi.raw,
                      mini = 1,
                      maxi = 7)

asi.df <- as.data.frame(asi.r)

# psych::alpha(asi.df)

# Overall ASI score
ASI <- multicon::composite(asi.df, rel=TRUE, nomiss = 0.6)
```

## Hostile Sexism
```{r}
# Higher values = more hostile sexism

host.raw <- data %>%
  dplyr::select(
    ASI_1,
    ASI_2,
    ASI_3,
    ASI_4,
    ASI_5,
    ASI_6,
    ASI_7,
    ASI_8,
    ASI_9,
    ASI_10,
    ASI_11
    )

host.key <- c(1, 1, 1, 1, 1,
             -1, -1, 1, -1, 1, 1)

host.r <- reverse.code(host.key,
                       host.raw,
                       mini= 1,
                       maxi = 7)

host.df <- as.data.frame(host.r)


Hostile <- multicon::composite(host.df, rel = TRUE, nomiss = 0.6)

```

## Benevolent Sexism
```{r}
# Higher values = more benevolent sexism

ben.raw <- data %>%
  dplyr::select(
    ASI_12,
    ASI_13,
    ASI_14,
    ASI_15,
    ASI_16,
    ASI_17,
    ASI_18,
    ASI_19,
    ASI_20,
    ASI_21,
    ASI_22
    )

ben.key <- c(1, 1, 1, -1,
             1, 1, 1, 1, -1,
             1, -1)

ben.r <- reverse.code(ben.key,
                      ben.raw,
                      mini=1,
                      maxi=7)

ben.df <- as.data.frame(ben.r)


Benevolent <- multicon::composite(ben.df, rel = TRUE, nomiss = 0.6)

```

# Correlations

## Victim Blaming 
```{r, results='asis'}

VicBlame.df <- data.frame(VictimBlaming, Invisibility, Invisibility1, Invisibility2, Invisibility3, CulturalRacism, RaceMini, NtvDehuman, Sovereignty, Ntvfeeling, Benevolent, Hostile, LibCon, Age, Violence)

corstars(VicBlame.df, result = "html")

# print(htmlTable::htmlTable(corstars(VicBlame.df, result = "html"),useViewer=TRUE))

```

## External Factors

```{r, results='asis'}
ExternalFactors.df <- data.frame(ExternalFactors, Invisibility, Invisibility1, Invisibility2, Invisibility3, CulturalRacism, RaceMini, NtvDehuman, Sovereignty, Ntvfeeling, Benevolent, Hostile, LibCon, Age, Violence)

corstars(ExternalFactors.df, result = "html")

# print(htmlTable::htmlTable(corstars(ExternalFactors.df, result = "html"),useViewer=TRUE))

```

## Community Blame 

```{r, results='asis'}
CommBlame.df <- data.frame(CommunityBlame, Invisibility, Invisibility1, Invisibility2, Invisibility3, CulturalRacism, RaceMini, NtvDehuman, Sovereignty, Ntvfeeling, Benevolent, Hostile, LibCon, Age, Violence)

corstars(CommBlame.df, result = "html")

# print(htmlTable::htmlTable(corstars(CommBlame.df, result = "html"),useViewer=TRUE))
```

## Support

```{r, results='asis'}
Support.df <- data.frame(Support, Invisibility, Invisibility1, Invisibility2, Invisibility3, CulturalRacism, RaceMini, NtvDehuman, Sovereignty, Ntvfeeling, Benevolent, Hostile, LibCon, Age, Violence)

corstars(Support.df, result = "html")

# print(htmlTable::htmlTable(corstars(Support.df, result = "html"),useViewer=TRUE))
```

## Familiarity with MMIWG

```{r, results='asis'}
MMIWG.df <- data.frame(MMIWG, Invisibility, Invisibility1, Invisibility2, Invisibility3, CulturalRacism, RaceMini, NtvDehuman, Sovereignty, Ntvfeeling, Benevolent, Hostile, LibCon, Age, Violence)

corstars(MMIWG.df, result = "html")

# print(htmlTable::htmlTable(corstars(MMIWG.df, result = "html"),useViewer=TRUE))
```

## Familiarity with MeToo

```{r, results='asis'}
MeToo.df <- data.frame(MeToo, Benevolent, Hostile, LibCon, Age)

corstars(MeToo.df, result = "html")

# print(htmlTable::htmlTable(corstars(MeToo.df, result = "html"),useViewer=TRUE))
```

# Tested Research Questions

How does the misunderstanding about Native people contribute to the epidemic of MMIWG?

1. How does misunderstanding about Native people contribute to victim blaming of MMIWG?
* When we add in cultural racism, invisibility is no longer significant - is there overlap in variability?

```{r}

VicBlame <- data.frame(VictimBlaming, Invisibility, Invisibility1, Invisibility2, Invisibility3, CulturalRacism, RaceMini, NtvDehuman, Sovereignty, Ntvfeeling, Benevolent, Hostile, LibCon, Age, Violence, MMIWG)

victimblame.model <- lm(VictimBlaming ~ 1 + Invisibility + RaceMini + Violence + Sovereignty + MMIWG, data = VicBlame)

summary(victimblame.model)

```


2. How does the misunderstanding about Native people contribute to taking into consideration external factors? 
+ Not that great, model accounts for only 10% of variability
```{r}

ExternFactor <- data.frame(ExternalFactors, Invisibility, Invisibility1, Invisibility2, Invisibility3, CulturalRacism, RaceMini, NtvDehuman, Sovereignty, Ntvfeeling, Benevolent, Hostile, LibCon, Age, Violence, MMIWG)

externalfactors.model <- lm(ExternalFactors ~ 1 + Invisibility + RaceMini + Violence + MMIWG, data = ExternFactor)

summary(externalfactors.model)

```

3. How does misunderstanding about Native people contribute to blaming the community for MMIWG?
```{r}

Commblame <- data.frame(CommunityBlame, Invisibility, Invisibility1, Invisibility2, Invisibility3, CulturalRacism, RaceMini, NtvDehuman, Sovereignty, Ntvfeeling, Benevolent, Hostile, LibCon, Age, Violence, MMIWG)

commblame.model <- lm(CommunityBlame ~ 1 + Invisibility + RaceMini + Violence + MMIWG, data = Commblame)

summary(commblame.model)

# Not that great, model accounts for only 10% of variability

```

4. How does misunderstanding about Native people contribute to support to end MMIWG?
* Racism minimization and knowledge about MMIWG, consistenly holding through each model 
* How do we think about invisibility and racism minization? Are they actually independent? 
```{r}
Supp <- data.frame(Support, Invisibility, Invisibility1, Invisibility2, Invisibility3, CulturalRacism, RaceMini, NtvDehuman, Sovereignty, Ntvfeeling, Benevolent, Hostile, LibCon, Age, Violence, MMIWG)

support.model <- lm(Support ~ 1 + Invisibility + RaceMini + Violence + MMIWG, data = Supp)

summary(support.model)
```

How does prejudice and racism towards Native people contribute to the epedemic of MMIWG?

1. How does prejudice and racism towards Native people contribute to victim blaming?
* Cultural Racism predicts victim blaming 
```{r}
vic.prej <- data.frame(VictimBlaming, CulturalRacism, NtvDehuman, data$NtvFeelings_31)

vic.prej.model <- lm(VictimBlaming ~ 1 + CulturalRacism + NtvDehuman + data$NtvFeelings_31, data = vic.prej)

summary(vic.prej.model)
```

2. How does prejudice and racism towards Native people contribute to taking into consideration external factors? 
* The more you dehumanize Natives, the more you take into consideration external factors - does not make sense
* R squared is only .031, not the best model - only accounting for 3% of variance 
```{r}
extern.prej <- data.frame(ExternalFactors, CulturalRacism, NtvDehuman, data$NtvFeelings_31)

extern.prej.model <- lm(ExternalFactors ~ 1 + CulturalRacism + NtvDehuman + data$NtvFeelings_31, data = vic.prej)

summary(extern.prej.model)
```

3. How does prejudice and racism towards Native people contribute to blaming the community? 
* 
```{r}
commblame.prej <- data.frame(CommunityBlame, CulturalRacism, NtvDehuman, data$NtvFeelings_31)

commblame.prej.model <- lm(CommunityBlame ~ 1 + CulturalRacism + NtvDehuman + data$NtvFeelings_31, data = commblame.prej)

summary(commblame.prej.model)
```

4. How does prejudice and racism towards Native people contribute to support to end MMIWG? 
* 
```{r}
supp.prej <- data.frame(Support, CulturalRacism, NtvDehuman, data$NtvFeelings_31)

supp.prej.model <- lm(Support ~ 1 + CulturalRacism + NtvDehuman + data$NtvFeelings_31, data = supp.prej)

summary(supp.prej.model)
```


How do broadly held sexist views contribute to the epidemic of MMIWG? How does this compare with knowledge about MeToo? 
1. How do sexist attitudes contribute to victim blaming of MMIWG?

```{r}
vicblame.sexism <- data.frame(VictimBlaming, ASI, Benevolent, Hostile)

vicblame_sexism_model <- lm(VictimBlaming ~ 1 + Benevolent + Hostile, data = vicblame.sexism)

summary(vicblame_sexism_model)
```
2. How do sexist attitudes contribute to consideration of external factors impacting MMIWG? 
```{r}
extern.sexism <- data.frame(ExternalFactors, ASI, Benevolent, Hostile)

extern_sexism_model <- lm(ExternalFactors ~ 1 + Benevolent + Hostile, data = extern.sexism)

summary(extern_sexism_model)
```
3. How do sexist attitudes contribute to blaming Native communities for MMIWG? 

```{r}
commblame.sexism <- data.frame(CommunityBlame, ASI, Benevolent, Hostile)

commblame_sexism_model <- lm(CommunityBlame ~ 1 + Benevolent + Hostile, data = commblame.sexism)

summary(commblame.prej.model)
```

4. How do sexist attitudes impact support to end MMIWG?

```{r}
supp_sexism <- data.frame(Support, ASI, Benevolent, Hostile, MMIWG, MeToo)

support_sexism_model <- lm(Support ~ 1 + Benevolent + Hostile, data = supp_sexism)

summary(support_sexism_model)

MeToo_sexism_model <- lm(MeToo ~ 1 + ASI, data = supp_sexism)

summary(MeToo_sexism_model)

MMIWG_sexism_model <- lm(MMIWG ~ 1 + ASI, data = supp_sexism)

summary(MMIWG_sexism_model)
```

4. How do broadly held sexist views contribute to knowledge of MeToo?

```{r}
MeToo_sexism <- data.frame(data$MeToo, ASI, Benevolent, Hostile)

MeToo_sexism_model <- lm(data$MeToo ~ 1 + Benevolent + Hostile, data = MeToo_sexism)

summary(MeToo_sexism_model)
```

# Mediation Analysis 

Invisibility
```{r}
allvars <- data.frame(Invisibility, RaceMini, Violence, Sovereignty, ASI, Benevolent, Hostile, VictimBlaming, CommunityBlame, ExternalFactors, Invisibility1, Invisibility2, Invisibility3, Support, WhiteDehuman)

mod.invisibility <- mediate(Support ~ Invisibility + (VictimBlaming) + (ExternalFactors), data = allvars)

summary(mod.invisibility)

```

Racism Minimization
```{r}
mod.racemini <- mediate(Support ~ RaceMini + (VictimBlaming) + (ExternalFactors), data = allvars)

summary(mod.racemini)

```

Violence 
```{r}
mod.violence <- mediate(Support ~ Violence + (VictimBlaming) + (CommunityBlame) + (ExternalFactors), data = allvars)

summary(mod.violence)
```

Knowledge about MMIWG
```{r}
mod.mmiwg <- mediate(Support ~ MMIWG + (VictimBlaming) + (CommunityBlame) + (ExternalFactors), data = allvars)

summary(mod.mmiwg)

```

Sovereignty 
```{r}
mod.sov <- mediate(Support ~ Sovereignty + (VictimBlaming) + (CommunityBlame) + (ExternalFactors), data = allvars)

summary(mod.sov)


corr.test(allvars$VictimBlaming, allvars$CommunityBlame)
```

```{r}
vars <- data.frame(VictimBlaming, ExternalFactors, WhiteDehuman, Support)

whitedehuman.sov <- mediate(Support ~ WhiteDehuman + (VictimBlaming) + (ExternalFactors), data = allvars)

summary(whitedehuman.sov)

dehum.support <- lm(Support ~ WhiteDehuman, data = vars)

summary(dehum.support)

dehum.invisibility <- lm(WhiteDehuman ~ Invisibility, data = vars)

dehum.invisibility <- lm(Invisibility ~ WhiteDehuman, data = vars)

summary(dehum.invisibility)

dehum.vicblame <- lm(VictimBlaming ~ WhiteDehuman, data = vars)
summary(dehum.vicblame)

dehum.structural <- lm(ExternalFactors ~ WhiteDehuman, data = vars)
summary(dehum.structural)
```

```{r}
sup.invisibility <- lm(Support ~ Invisibility, data = vars)

summary(sup.invisibility)
```

```{r}
ggplot(data = vars, aes(x = Invisibility, y = Support)) + geom_point() + geom_abline()

ggplot(vars, aes(Invisibility, Support)) + geom_point() + geom_abline()
```

```{r}
install.packages("lavaan")
require(lavaan)

X <- vars$Support
M1 <- vars$VictimBlaming
M2 <- vars$ExternalFactors
Y <- vars$WhiteDehuman

mediate.data <- data.frame(X = X, Y = X, M1 = M1, M2 = M2)

multipleMediation <- '
    Y ~ b1 * M1 + b2 * M2 + c * X
    M1 ~ a1 * X
    M2 ~ a2 * X
    indirect1 := a1 * b1
    indirect2 := a2 * b2
    total    := c + (a1 * b1) + (a2 * b2)
    M1 ~~ M2 
'
fit <- sem(model = multipleMediation, data = mediate.data)
summary(fit)


```


```{r}

```

