---
title: "MMIWG1 Descriptive Statistics (Updated w/Julisa Code)"
author: "Jamie Yellowtail"
date: "9/8/2019"
output: word_document
editor_options: 
  chunk_output_type: console
---
```{r}
## Necessary Packages
#{r load packages}
library(psych) # For reverse coding variables, reading data files and item analysis
library(multicon) # For creating composites
library(tidyverse)
#install.packages("haven")
library(haven)
#install.packages("labelled")
library(labelled)
#install.packages("nFactors")
library(nFactors) # Determines how many factors to extract
library(dplyr) #clean up data
#install.packages("corrplot")
library(corrplot) # For correlation matrix
library(GGally)
#install.packages("Rmisc") #Multiplot
library(Rmisc)

```

## Functions to center things
```{r functions}

center<-function(MOD)
{
  centered<-MOD-mean(MOD,na.rm=TRUE)
  return(centered)
}

low<-function(MOD)
{
  low<-(MOD-mean(MOD,na.rm=TRUE))+sd(MOD, na.rm=TRUE)
  return(low)
}

high<-function(MOD)
{
  high<-(MOD-mean(MOD, na.rm=TRUE))-sd(MOD, na.rm=TRUE)
  return(high)
}

gmc <- function(MOD, grp)
  {
  gmcentered<- (MOD-tapply(MOD,grp,mean,na.rm=TRUE)[grp])
  return(gmcentered)

}

```

## Prepping Data File
```{r Read Data File}

data <- read.csv("MMIWG.csv")

data <- data %>% 
  dplyr::rename(Mauna_Kea = Movements_16)

#view(data)
```

#Knowledge of Social Movements
```{r}
#Social Movements
SocialMovements.df <- data.frame(data$MeToo,
                data$March4lives,
                data$BLM,
                data$AllLives,
                data$ZeroHour,
                data$BlueLives,
                data$MenRights,
                data$WhiteNationa,
                data$StraightPride,
                data$LGBTQ,
                data$Right2Life,
                data$Timesup,
                data$MMIWG,
                data$NativeLives,
                data$NODAPL,
                data$Mauna_Kea)

psych::alpha(SocialMovements.df, check.keys = TRUE)

SocialMovements.comp <- multicon::composite(SocialMovements.df, rel=TRUE, nomiss = 0)

#Native Social Movements
NativeSM.df <- data.frame(data$MMIWG,
                data$NativeLives,
                data$NODAPL,
                data$Mauna_Kea)

psych::alpha(NativeSM.df, check.keys = TRUE)

NativeSM.comp <- multicon::composite(NativeSM.df, rel=TRUE, nomiss = 0)

#Non-Native Social Movements
NonNativeSM.df <- data.frame(data$MeToo,
                data$March4lives,
                data$BLM,
                data$AllLives,
                data$ZeroHour,
                data$BlueLives,
                data$MenRights,
                data$WhiteNationa,
                data$StraightPride,
                data$LGBTQ,
                data$Right2Life,
                data$Timesup)

psych::alpha(NonNativeSM.df, check.keys = TRUE)

NonNativeSM.comp <- multicon::composite(NonNativeSM.df, rel=TRUE, nomiss = 0)

#POC Centered Social Movements
POCSM.df <- data.frame(data$BLM,
                data$MMIWG,
                data$NativeLives,
                data$NODAPL,
                data$Mauna_Kea)

psych::alpha(POCSM.df, check.keys = TRUE)

POCSM.comp <- multicon::composite(POCSM.df, rel=TRUE, nomiss = 0)

#NonPOC Centered Social Movements
NonPOCSM.df <- data.frame(data$MeToo,
                data$March4lives,
                data$AllLives,
                data$ZeroHour,
                data$BlueLives,
                data$MenRights,
                data$WhiteNationa,
                data$StraightPride,
                data$LGBTQ,
                data$Right2Life,
                data$Timesup)

psych::alpha(NonPOCSM.df, check.keys = TRUE)

NonPOCSM.comp <- multicon::composite(NonPOCSM.df, rel=TRUE, nomiss = 0)

#Liberal Associated Social Movements
LiberalSM.df <- data.frame(data$MeToo,
                data$March4lives,
                data$BLM,
                data$ZeroHour,
                data$LGBTQ,
                data$Timesup,
                data$MMIWG,
                data$NativeLives,
                data$NODAPL,
                data$Mauna_Kea)

psych::alpha(LiberalSM.df, check.keys = TRUE)

LiberalSM.comp <- multicon::composite(LiberalSM.df, rel=TRUE, nomiss = 0)

#Conservative Associated Social Movements
ConservSM.df <- data.frame(data$AllLives,
                data$BlueLives,
                data$MenRights,
                data$WhiteNationa,
                data$StraightPride,
                data$Right2Life)

psych::alpha(ConservSM.df, check.keys = TRUE)

ConservSM.comp <- multicon::composite(ConservSM.df, rel=TRUE, nomiss = 0)

#Environmental Social Movements
EnvirSM.df <- data.frame(data$ZeroHour,
                data$NativeLives,
                data$NODAPL,
                data$Mauna_Kea)

psych::alpha(EnvirSM.df, check.keys = TRUE)

EnvirSM.comp <- multicon::composite(EnvirSM.df, rel=TRUE, nomiss = 0)

#Women's Social Movements
WomenSM.df <- data.frame(data$MeToo,
                data$Timesup,
                data$MMIWG)

psych::alpha(WomenSM.df, check.keys = TRUE)

WomenSM.comp <- multicon::composite(WomenSM.df, rel=TRUE, nomiss = 0)

```

# How did you become familiar with MMIWG?

```{r}
source_raw.df <- data.frame(data$IF_FAMILIAR_1,
                data$IF_FAMILIAR_2,
                data$IF_FAMILIAR_3,
                data$IF_FAMILIAR_6,
                data$IF_FAMILIAR_7,
                data$IF_FAMILIAR_8,
                data$IF_FAMILIAR_10,
                data$IF_FAMILIAR_11,
                data$IF_FAMILIAR_13,
                data$IF_FAMILIAR_14,
                data$IF_FAMILIAR_15)

source_count <- colSums(source_raw.df, na.rm=TRUE)
source_count

plot(source_count, type = "h")

```

# What is your primary source of information on MMIWG?
```{r}
primsource <- (table(data$SourceOnMMIWG))

plot(primsource)
```
#Attitudes and Beliefs that Contribute to MMIWG
```{r}
# higher signifies more negative attitudes

att <- data %>%
  dplyr::select(
    AB_Activists,
    AB_SexWork,
    AB_NonNative_pers,
    AB_Rez,
    AB_Citizens,
    AB_Runaways,
    AB_Drug,
    AB_MaleWorker,
    AB_Criminal,
    AB_TwoParent,
    AB_TribalPolice,
    AB_Poverty,
    AB_NativeComm,
    AB_Society,
    AB_Abusive,
    AB_Laws
    )

att.key = c(1, 1, -1, 1, -1, 1, 1, -1,
               1, 1, -1, 1, 1, 1, 1, -1) #Reverse Scoring

att.r <-
  reverse.code(att.key,
               att,
               mini = 1,
               maxi = 7)

att.df <- as.data.frame(att.r)

att.df[is.na(att.df)] <- 0

```

# Item analysis of Attitudes
```{r}
psych::alpha(att.df, check.keys = TRUE)

att.comp <- multicon::composite(att.df, rel=TRUE, nomiss = 0)
```

# Determining the number of factors to extract
```{r}
ev.att <- eigen(cor(att.df))
ap.att <- parallel(subject=nrow(att.df),var=ncol(att.df),
               rep = 100, cent = .05)
nS.att <- nScree(x=ev.att$values, apparallel = ap.att$eigen$qevpea)
plotnScree(nS.att)
```

# Factor loadings
```{r}
fit.att <- factanal(att.df, 3, rotation = "varimax")
print(fit.att, digits = 2, cutoff = .3, sort = TRUE)
```

1. Factor 1 - Victim Blaming
+ MMIWG are not as big of a problem as activists would like people to think.
+ MMIWG were involved in sex work.
+ MMIWG only takes place on the reservation.
+ MMIWG under 18 were runaways.
+ MMIWG were using drugs and/or alcohol.
+ MMIWG were involved in criminal activity.

2. Factor 2 - Institution level and outside factors
+ MMIWG are a result of violence perpetrated by non-Natives.
+ Ending the MMIWG crisis is the responsibility of all U.S. citizens.
+ Non-native male workers that live near reservations contribute to the high rates of  MMIWG.
+ Tribal police forces do not have the resources to prevent + Native women from being murdered and going missing.
+ Policies and laws that make it difficult to prosecute Non-native offenders contribute to the epidemic of MMIWG.

3. Factor 3 - Community issue
+ The lack of two parent homes in tribal communities puts Native American girls at risk of going missing.
+ MMIWG are the result of poverty within Native communities.
+ Native women are murdered and go missing because Native communities do not value Native women.
+ MMIWG under 18 come from abusive homes.
+ Native women are murdered and go missing because U.S. society does not value Native women.

# Victim Blaming subscale
```{r}
vicblame.raw <- data %>%
  dplyr::select(
    AB_Activists,
    AB_SexWork,
    AB_Rez,
    AB_Runaways,
    AB_Drug,
    AB_Criminal
    )

vicblame.key <- c(1, 1, 1, 1, 1, 1)

vicblame.r <- reverse.code(vicblame.key,
                           vicblame.raw,
                           mini = 1,
                           maxi = 7)

vicblame.df <- as.data.frame(vicblame.r)

vicblame.comp <- multicon::composite(vicblame.df, rel=TRUE, nomiss = 0)
```

# External Factors subscale
```{r}
externfactors.raw <- data %>%
  dplyr::select(
    AB_NonNative_pers,
    AB_Citizens,
    AB_MaleWorker,
    AB_TribalPolice,
    AB_Laws
    )

externfactors.key <- c(-1, -1, -1, -1, -1)

externfactors.r <- reverse.code(externfactors.key,
                                externfactors.raw,
                                mini=1,
                                maxi=7)

externfactors.df <- as.data.frame(externfactors.r)

externfactors.comp <- multicon::composite(externfactors.df, rel = TRUE, nomiss=0)
```

# Community Blame subscale
```{r}

commblame.raw <- data %>%
  dplyr::select(
    AB_TwoParent,
    AB_Poverty,
    AB_NativeComm,
    AB_Abusive,
    AB_Society
    )

commblame.key <- c(1, 1, 1, 1, 1)

commblame.r <-
  reverse.code(commblame.key,
               commblame.raw,
               mini = 1,
               maxi = 7)

commblame.df <- as.data.frame(commblame.r)

commblame.comp <- multicon::composite(commblame.df, rel = TRUE, nomiss = 0)

```

#Support for MMIWG
```{r}
# Higher values = more support

sup <- data %>%
  dplyr::select(Sup_Hash,
                Sup_Letter,
                Sup_Donate,
                Sup_Authority,
                Sup_Prosecute,
                Sup_Access,
                Sup_Training
                )

sup.df <- as.data.frame(sup)

sup.df[is.na(sup.df)] <- 0
```

#Determining the number of factors to extract
```{r}
ev.sup <- eigen(cor(sup.df))
ap.sup <- parallel(subject=nrow(sup.df),var=ncol(sup.df),
               rep = 100, cent = .05)
nS.sup <- nScree(x=ev.sup$values, apparallel = ap.sup$eigen$qevpea)
plotnScree(nS.sup)
```

# Factor Loadings
```{r}
fit.sup <- factanal(sup.df, 1, rotation = "varimax")
print(fit.sup, digits = 2, cutoff = .3, sort = TRUE)
```

#Item and overall analysis of support (5 point scale, Def not to Def)
```{r}
psych::alpha(sup.df, check.keys = TRUE)

sup.com <-
  multicon::composite(sup,
  rel = TRUE,
  nomiss = 0)

```

# Who is responsible for stopping the epidemic of MMIWG?
```{r}
stop.df <- data.frame(data$Res_Stopping_1,
                       data$Res_Stopping_2,
                       data$Res_Stopping_3,
                       data$Res_Stopping_4)

psych::alpha(stop.df, check.keys = TRUE)

stop.comp <-
  multicon::composite(stop.df,
  rel = TRUE,
  nomiss = 0)
```

# Who is responsible for preventing individual MMIWG attacks?
```{r}
prev.df <- data.frame(data$Res_Preventing_1,
                      data$Res_Preventing_2,
                      data$Res_Preventing_3,
                      data$Res_Preventing_4
                      )
prev.comp <-
  multicon::composite(prev.df,
  rel = TRUE,
  nomiss = 0)
psych::alpha(prev.df, check.keys = TRUE)
```

# Who is responsible for bringing awareness to MMIWG?
```{r}
awar.df <- data.frame(data$Res_Awareness_1,
                      data$Res_Awareness_2,
                      data$Res_Awareness_3,
                      data$Res_Awareness_4
                      )
awar.comp <-
  multicon::composite(awar.df,
  rel = TRUE,
  nomiss = 0)
psych::alpha(awar.df, check.keys = TRUE)
```

#Invisibility
```{r}
# Higher values = greater invisibility

data.in <- data %>%
  dplyr::rename(NtvInvisibility_7 = Invisibility1_13,
         NtvInvisibility_8 = Invisibility1_14,
         NtvInvisibility_9 = Invisibility1_15,
         NtvInvisibility_10 = Invisibility1_16,
         NtvInvisibility_11 = Invisibility1_17,
         NtvInvisibility_12 = Invisibility1_18)

in.raw <- data.in %>%
  dplyr::select(
    NtvInvisibility_1,
    NtvInvisibility_2,
    NtvInvisibility_3,
    NtvInvisibility_4,
    NtvInvisibility_5,
    NtvInvisibility_6,
    NtvInvisibility_7,
    NtvInvisibility_8,
    NtvInvisibility_9,
    NtvInvisibility_10,
    NtvInvisibility_11,
    NtvInvisibility_12,
    IN_Violence
    )

in.key <- c(1, -1, 1, 1,
           1, 1, 1, -1,
           1, 1, 1, 1, 1)

in.r <-
  reverse.code(in.key,
               in.raw,
               mini = 1,
               maxi = 7)

in.df <- as.data.frame(in.r)

in.df[is.na(in.df)] <- 0

```

# Determining number of factors to extract
```{r}
ev.in <- eigen(cor(in.df))
ap.in <- parallel(subject=nrow(in.df),var=ncol(in.df),
               rep = 100, cent = .05)
nS.in <- nScree(x=ev.in$values, apparallel = ap.in$eigen$qevpea)
plotnScree(nS.in)
```

# Factor loadings
```{r}
fit.in <- factanal(in.df, 3, rotation = "varimax")
print(fit.in, digits = 2, cutoff = .3, sort = TRUE)
```

Factor 1 - Individual perceptions
+ I rarely think about Native/Indigenous Americans in contemporary society.
+ When I think about poverty, Native/Indigenous Americans do not come to mind.
+ When I think about groups that experience racism and discrimination Native/Indigenous Americans do not come to mind.
+ When I think about successful Americans, Native/Indigenous do not come to mind.
+ When I think about actors and actresses, Native/Indigenous Americans do not come to mind.
+ When I think about healthy families, Native/Indigenous Americans do not come to mind.
+ When I think of violence against women, Native women do not come to mind.

Factor 2
+ Native/Indigenous Americans are invisible in contemporary society.
+ I rarely hear about Native/Indigenous Americans in contemporary society.

Factor 3
+ There are hardly any Native/Indigenous Americans left in U.S. society.
+ In contemporary society, there are not any real  Native/Indigenous Americans.

Factor 4
+ There is a significant number of Native/Indigenous Americans who live in U.S. society today.
+ When I think about health disparities, Native/Indigenous Americans come to mind.

# Item analysis
```{r}
psych::alpha(in.df, check.keys = TRUE)

in.com <-
  multicon::composite(in.df,
  rel = TRUE,
  nomiss = 0)
```

# Sovereignty
```{r}
# Higher values = more knowledge about sovereignty

sov.raw <- data %>%
  dplyr::select(
    Sov_Rules,
    Sov_Legal,
    Sov_Police,
    Sov_Gov,
    Sov_Auto,
    Sov_Rely,
    Sov_Jurisdiction)

sov.key <- c(1, -1, 1, 1,
             1, -1, -1)

sov.r <- reverse.code(sov.key,
                      sov.raw,
                      mini = 1,
                      maxi = 7)

sov.df <- as.data.frame(sov.r)

sov.df[is.na(sov.df)] <- 0

```

# Determining number of factors to extract
```{r}
ev.sov <- eigen(cor(sov.df))
ap.sov <- parallel(subject=nrow(sov.df),var=ncol(sov.df),
               rep = 100, cent = .05)
nS.sov <- nScree(x=ev.sov$values, apparallel = ap.sov$eigen$qevpea)
plotnScree(nS.sov)
```

# Factor loadings
```{r}
fit.sov <- factanal(sov.df, 2, rotation = "varimax")
print(fit.sov, digits = 2, cutoff = .3, sort = TRUE)
```
Factor 1 - Natives are sovereign
+ Native American tribes create and enforce their own rules, policies, and laws on reservations.
+ Native American tribes manage their own police forces.
+ Native American tribes determine the nature/structure of their own government without interference from U.S. or state governments.
+ Native American tribes are self-governing, autonomous nations within the United States.

Factor 2
+ Native American tribes do not have control over their own judicial and legal systems.
+ Native American tribal police do not have jurisdiction over all people who reside on or are located on their reservation.
+ Native Americans tribes rely on the U.S. government to function as a nation.


# Item analysis
```{r}
psych::alpha(sov.df, check.keys = TRUE)

sov.comp <-
  multicon::composite(sov.df,
  rel = TRUE,
  nomiss = 0)

#view(sov.comp)
```

#Sovereign Statements
```{r}
sov1.raw <- data %>%
  dplyr::select(
    Sov_Rules,
    Sov_Police,
    Sov_Gov,
    Sov_Auto
    )

sov1.key <- c(1, 1, 1, 1)

sov1.r <-
  reverse.code(sov1.key,
               sov1.raw,
               mini = 1,
               maxi = 7)

sov1.df <- as.data.frame(sov1.r)

sov1.comp <- multicon::composite(sov1.df, rel = TRUE, nomiss = 0)
```

#Not Sovereign Statements
```{r}
sov2.raw <- data %>%
  dplyr::select(
    Sov_Legal,
    Sov_Rely,
    Sov_Jurisdiction)

sov2.key <- c(-1, -1, -1)

sov2.r <-
  reverse.code(sov2.key,
               sov2.raw,
               mini = 1,
               maxi = 7)

sov2.df <- as.data.frame(sov2.r)

sov2.comp <- multicon::composite(sov2.df, rel = TRUE, nomiss = 0)
```

# Racism Minimization
```{r}
# Higher values = Greater minimization of racism

racemini.raw <- data %>%
  dplyr::select(
    RacismMini_1,
    RacismMini_2,
    RacismMini_3,
    RacismMini_4,
    RacismMini_5,
    RacismMini_6,
    RacismMini_7,
    RacismMini_8,
    RacismMini_9,
    RacismMini_10
    )

racemini.key <- c(1, -1, 1, -1, -1,
                  -1, -1, 1, 1, 1)

racemini.r <- reverse.code(racemini.key,
                           racemini.raw,
                           mini = 1,
                           maxi = 7)

racemini.df <- as.data.frame(racemini.r)

racemini.comp <-
  multicon::composite(racemini.df, rel = TRUE, nomiss = 0)

psych::alpha(racemini.df, check.keys = TRUE)

```

# Cultural Racism
```{r}
# Higher values = More cultural racism

culturalracism.raw <- data %>%
  dplyr::select(
    CulturalRacism_1,
    CulturalRacism_2,
    CulturalRacism_3,
    CulturalRacism_4,
    CulturalRacism_5,
    CulturalRacism_6,
    CulturalRacism_7,
    CulturalRacism_8,
    CulturalRacism_9,
    CulturalRacism_10,
    CulturalRacism_11,
    CulturalRacism_12,
    CulturalRacism_13
    )

culrac.key <- c(1, 1, 1, 1, -1,
                -1, 1, 1, 1, 1,
                1, 1, 1)

culturalracism.r <- reverse.code(culrac.key,
                                 culturalracism.raw,
                                 mini = 1,
                                 maxi = 7)

culturalracism.df <- as.data.frame(culturalracism.r)

```

# Item analysis
```{r}
psych::alpha(culturalracism.df, check.keys = TRUE)

culturalracism.comp <-
  multicon::composite(culturalracism.df,
  rel = TRUE,
  nomiss = 0)
```

# Native Dehumanization
```{r}
ntvdehum.raw <- data %>%
  dplyr::select(NtvDehum_1,
                NtvDehum_2,
                NtvDehum_3,
                NtvDehum_4,
                NtvDehum_5,
                NtvDehum_6,
                NtvDehum_7,
                NtvDehum_8)

ntvdehum.key <- c(1, 1, 1, 1, -1,
                1, 1, 1)

ntvdehum.r <- reverse.code(ntvdehum.key,
                                 ntvdehum.raw,
                                 mini = 0,
                                 maxi = 100)

ntvdehum.df <- as.data.frame(ntvdehum.r)

psych::alpha(ntvdehum.df, check.keys = TRUE)

ntvdehum.comp <-
  multicon::composite(ntvdehum.df,
  rel = TRUE,
  nomiss = 0)
```

# White Dehumanization
```{r}

whitedehum.raw <- data %>%
  dplyr::select(
    WhiteDehuman_1,
    WhiteDehuman_2,
    WhiteDehuman_3,
    WhiteDehuman_4,
    WhiteDehuman_5,
    WhiteDehuman_6,
    WhiteDehuman_7,
    WhiteDehuman_8
    )
whitedehum.key <- c(1, 1, 1, 1, -1,
                1, 1, 1)

whitedehum.r <- reverse.code(whitedehum.key,
                                 whitedehum.raw,
                                 mini = 0,
                                 maxi = 100)

whitedehum.df <- as.data.frame(whitedehum.r)
whitedehum.comp <-
  multicon::composite(whitedehum.df,
  rel = TRUE,
  nomiss = 0)

psych::alpha(whitedehum.df)
```

# Native Feelings thermometer
```{r}
describe(data$NtvFeelings_31)
summary(data$NtvFeelings_31)

```

# White Feelings Thermometer
```{r}
describe(data$White_thermo_31)
summary(data$White_thermo_31)

```

# ASI
```{r}
asi.raw <- data %>%
  dplyr::select(
    ASI_1,
    ASI_2,
    ASI_3,
    ASI_4,
    ASI_5,
    ASI_6,
    ASI_7,
    ASI_8,
    ASI_9,
    ASI_10,
    ASI_11,
    ASI_12,
    ASI_13,
    ASI_14,
    ASI_15,
    ASI_16,
    ASI_17,
    ASI_18,
    ASI_19,
    ASI_20,
    ASI_21,
    ASI_22
    )

asi.key <- c(1, 1, 1, 1, 1,
             -1, -1, 1, -1, 1,
             1, 1, 1, 1, -1,
             1, 1, 1, 1, -1,
             1, -1)

asi.r <- reverse.code(asi.key,
                      asi.raw,
                      mini = 1,
                      maxi = 7)

asi.df <- as.data.frame(asi.r)
 
```

# Determining the number of factors to extract
```{r}
ev.asi <- eigen(cor(asi.df))
ap.asi <- parallel(subject=nrow(asi.df),var=ncol(asi.df),
               rep = 100, cent = .05)
nS.asi <- nScree(x=ev.asi$values, apparallel = ap.asi$eigen$qevpea)
plotnScree(nS.asi)
```

# Factor loadings
```{r}
fit.asi <- factanal(asi.df, 3, rotation = "varimax")
print(fit.asi, digits = 2, cutoff = .3, sort = TRUE)

```

# ASI Descriptives
```{r}
# Item analysis

psych::alpha(asi.df)

# Overall ASI score
asi.comp <- multicon::composite(asi.df, rel=TRUE, nomiss = 0)

# ASI subscale - Hostile Sexism

host.raw <- data %>%
  dplyr::select(
    ASI_1,
    ASI_2,
    ASI_3,
    ASI_4,
    ASI_5,
    ASI_6,
    ASI_7,
    ASI_8,
    ASI_9,
    ASI_10,
    ASI_11
    )

host.key <- c(1, 1, 1, 1, 1,
             -1, -1, 1, -1, 1, 1)

host.r <- reverse.code(host.key,
                       host.raw,
                       mini= 1,
                       maxi = 7)

host.df <- as.data.frame(host.r)

host.comp <- multicon::composite(host.df, rel = TRUE, nomiss = 0)

# ASI subscale - Benevolent Sexism

ben.raw <- data %>%
  dplyr::select(
    ASI_12,
    ASI_13,
    ASI_14,
    ASI_15,
    ASI_16,
    ASI_17,
    ASI_18,
    ASI_19,
    ASI_20,
    ASI_21,
    ASI_22
    )

ben.key <- c(1, 1, 1, -1,
             1, 1, 1, 1, -1,
             1, -1)

ben.r <- reverse.code(ben.key,
                      ben.raw,
                      mini=1,
                      maxi=7)

ben.df <- as.data.frame(ben.r)

ben.comp <- multicon::composite(ben.df, rel = TRUE, nomiss = 0)

```

# Demographics

#Race
```{r}
table(data$Race)

head(data$Race)
```

#Gender
```{r}

table(data$Gender)
#Gender: Male- 166; Females-114; N/A-20
#***No entries: Transgender man, Transgender woman, Non-binary, Genderqueer

```

# SES - highest level of education

```{r}
table(data$SES)

# HS Diploma = 73
# AA = 45
# BA/BS = 132
# MA/MS = 26
# Doctorate = 5
```

# Born in US

```{r}
table(data$BorninUS)
#Born in the US: Yes- 269; No-12; N/A- 19
```

# Citizen

```{r}
table(data$Citizen)
#No-3 Yes-9; N/A- 288
```

#Age
```{r}
table(data$Age.r)
summary(data$Age.r)
#Age: Mean= 35.98;  SD=16;  Min=19 Max= 69

stem(data$Age.r)

AgeGroups <- cut(data$Age.r, breaks=c(18, 24, 34, 44, Inf), labels=c("18-24", "25-34", "35-44", "45+"))

```

#Liberal/Conservative
```{r}
table(data$LibCon)
summary(data$LibCon)

#Liberal/Conservative: Extremely Conservative:20; Conservative:26; Somewhat Conservative:21; Moderate:69; Somewhat Liberal:42; Liberal:51; Extremely Liberal: 49; NA: 22
```
#News Source
```{r}
(primnews <- (table(data$NewsSource)))
plot(primnews)

#Primary News Source: National TV: 76; Local TV: 20; Social Media: 97; Radio/Podcast: 13; Online Blog: 23; National Newspaper: 33; Local Newspaper: 7; Published Research Report: 4; Word of Mouth: 6; Unsure: 2; N/A: 19
```

# Correlations
```{r}
#Summary of Variables
SumVariables.df<- data.frame(SocialMovements.comp, NativeSM.comp, NonNativeSM.comp, POCSM.comp, NonPOCSM.comp, LiberalSM.comp, ConservSM.comp, EnvirSM.comp, WomenSM.comp, att.comp, vicblame.comp, externfactors.comp, commblame.comp, sup.com, in.com, sov.comp, racemini.comp, culturalracism.comp, ntvdehum.comp, whitedehum.comp, asi.comp, host.comp, ben.comp, data$Age.r, data$SES, data$LibCon)

ggcorr(SumVariables.df,
       label = TRUE)

corr.test(SumVariables.df, y = NULL, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=FALSE,minlength=5)

```
#Attitudes and Beliefs Correlations
```{r}
#Attitudes and Beliefs/Social Movements
AB_and_SM <- corr.test(att.comp, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Native Social Movements
AB_and_NatSM <- corr.test(att.comp, y = NativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Non-Native Social Movements
AB_and_NonNatSM <- corr.test(att.comp, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/POC Social Movements
AB_and_POCSM <- corr.test(att.comp, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/NonPOC Social Movements
AB_and_NonPOCSM <- corr.test(att.comp, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Liberal Social Movements
AB_and_LiberalSM <- corr.test(att.comp, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Conservative Social Movements
AB_and_ConservSM <- corr.test(att.comp, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Environmental Social Movements
AB_and_EnvirSM <- corr.test(att.comp, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Women Centered Social Movements
AB_and_WomenSM <- corr.test(att.comp, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Support
AB_and_Support <- corr.test(att.comp, y = sup.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Invisibility
AB_and_Invisibility <- corr.test(att.comp, y = in.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Sovereignty
AB_and_Sovereignty <- corr.test(att.comp, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Race Minimization
AB_and_RaceMini <- corr.test(att.comp, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Cultural Racism
AB_and_CRacism <- corr.test(att.comp, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/Native Dehumanization
AB_and_NtvDehum <- corr.test(att.comp, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/ White Dehumanization
AB_and_WhiteDehum <- corr.test(att.comp, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/ Ambivalent Sexism Inventory
AB_and_ASI <- corr.test(att.comp, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/ Hostile Sexism
AB_and_HS <- corr.test(att.comp, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/ Benevolent Sexism
AB_and_BS <- corr.test(att.comp, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/ Age
AB_and_Age <- corr.test(att.comp, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/ SES
AB_and_SES <- corr.test(att.comp, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Attitudes and Beliefs/ Liberalism-Conservatism
AB_and_LibCon <- corr.test(att.comp, y = data$LibCon, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

```
#Victim Blaming Correlations
```{r}
#Victim Blaming/Social Movements
VB_and_SM <- corr.test(vicblame.comp, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Native Social Movements
VB_and_NatSM <- corr.test(vicblame.comp, y = NativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Non-Native Social Movements
VB_and_NonNatSM <- corr.test(vicblame.comp, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/POC Social Movements
VB_and_POCSM <- corr.test(vicblame.comp, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/NonPOC Social Movements
VB_and_NonPOCSM <- corr.test(vicblame.comp, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Liberal Social Movements
VB_and_LiberalSM <- corr.test(vicblame.comp, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Conservative Social Movements
VB_and_ConservSM <- corr.test(vicblame.comp, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Environmental Social Movements
VB_and_EnvirSM <- corr.test(vicblame.comp, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Women Centered Social Movements
VB_and_WomenSM <- corr.test(vicblame.comp, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Support
VB_and_Support <- corr.test(vicblame.comp, y = sup.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Invisibility
VB_and_Invisibility <- corr.test(vicblame.comp, y = in.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Sovereignty
VB_and_Sovereignty <- corr.test(vicblame.comp, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Race Minimization
VB_and_RaceMini <- corr.test(vicblame.comp, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Cultural Racism
VB_and_CRacism <- corr.test(vicblame.comp, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/Native Dehumanization
VB_and_NtvDehum <- corr.test(vicblame.comp, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/ White Dehumanization
VB_and_WhiteDehum <- corr.test(vicblame.comp, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/ Ambivalent Sexism Inventory
VB_and_ASI <- corr.test(vicblame.comp, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/ Hostile Sexism
VB_and_HS <- corr.test(vicblame.comp, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/ Benevolent Sexism
VB_and_BS <- corr.test(vicblame.comp, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/ Age
VB_and_Age <- corr.test(vicblame.comp, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/ SES
VB_and_SES <- corr.test(vicblame.comp, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Victim Blaming/ Liberalism-Conservatism
VB_and_LibCon <- corr.test(vicblame.comp, y = data$LibCon, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)
```
#External Factors Correlations
```{r}
#External Factors/Social Movements
EF_and_SM <- corr.test(externfactors.comp, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Native Social Movements
EF_and_NatSM <- corr.test(externfactors.comp, y = NativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Non-Native Social Movements
EF_and_NonNatSM <- corr.test(externfactors.comp, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/POC Social Movements
EF_and_POCSM <- corr.test(externfactors.comp, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/NonPOC Social Movements
EF_and_NonPOCSM <- corr.test(externfactors.comp, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Liberal Social Movements
EF_and_LiberalSM <- corr.test(externfactors.comp, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Conservative Social Movements
EF_and_ConservSM <- corr.test(externfactors.comp, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Environmental Social Movements
EF_and_EnvirSM <- corr.test(externfactors.comp, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Women Centered Social Movements
EF_and_WomenSM <- corr.test(externfactors.comp, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Support
EF_and_Support <- corr.test(externfactors.comp, y = sup.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Invisibility
EF_and_Invisibility <- corr.test(externfactors.comp, y = in.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Sovereignty
EF_and_Sovereignty <- corr.test(externfactors.comp, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Race Minimization
EF_and_RaceMini <- corr.test(externfactors.comp, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Cultural Racism
EF_and_CRacism <- corr.test(externfactors.comp, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/Native Dehumanization
EF_and_NtvDehum <- corr.test(externfactors.comp, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/ White Dehumanization
EF_and_WhiteDehum <- corr.test(externfactors.comp, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/ Ambivalent Sexism Inventory
EF_and_ASI <- corr.test(externfactors.comp, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/ Hostile Sexism
EF_and_HS <- corr.test(externfactors.comp, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/ Benevolent Sexism
EF_and_BS <- corr.test(externfactors.comp, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/ Age
EF_and_Age <- corr.test(externfactors.comp, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/ SES
EF_and_SES <- corr.test(externfactors.comp, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#External Factors/ Liberalism-Conservatism
EF_and_LibCon <- corr.test(externfactors.comp, y = data$LibCon, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)
```
#Community Blame Corelations
```{r}
#Community Blame/Social Movements
CB_and_SM <- corr.test(commblame.comp, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Native Social Movements
CB_and_NatSM <- corr.test(commblame.comp, y = NativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Non-Native Social Movements
CB_and_NonNatSM <- corr.test(commblame.comp, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/POC Social Movements
CB_and_POCSM <- corr.test(commblame.comp, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/NonPOC Social Movements
CB_and_NonPOCSM <- corr.test(commblame.comp, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Liberal Social Movements
CB_and_LiberalSM <- corr.test(commblame.comp, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Conservative Social Movements
CB_and_ConservSM <- corr.test(commblame.comp, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Environmental Social Movements
CB_and_EnvirSM <- corr.test(commblame.comp, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Women Centered Social Movements
CB_and_WomenSM <- corr.test(commblame.comp, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Support
CB_and_Support <- corr.test(commblame.comp, y = sup.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Invisibility
CB_and_Invisibility <- corr.test(commblame.comp, y = in.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Sovereignty
CB_and_Sovereignty <- corr.test(commblame.comp, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Race Minimization
CB_and_RaceMini <- corr.test(commblame.comp, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Cultural Racism
CB_and_CRacism <- corr.test(commblame.comp, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/Native Dehumanization
CB_and_NtvDehum <- corr.test(commblame.comp, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/ White Dehumanization
CB_and_WhiteDehum <- corr.test(commblame.comp, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/ Ambivalent Sexism Inventory
CB_and_ASI <- corr.test(commblame.comp, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/ Hostile Sexism
CB_and_HS <- corr.test(commblame.comp, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/ Benevolent Sexism
CB_and_BS <- corr.test(commblame.comp, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/ Age
CB_and_Age <- corr.test(commblame.comp, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/ SES
CB_and_SES <- corr.test(commblame.comp, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Community Blame/ Liberalism-Conservatism
CB_and_LibCon <- corr.test(commblame.comp, y = data$LibCon, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)
```

#Native Social Movements Correlations
```{r}
#Native SM/Social Movements
NatSM_and_SM <- corr.test(NativeSM.comp, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Native SM/Non-Native Social Movements
NatSM_and_NonNatSM <- corr.test(NativeSM.comp, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/POC Social Movements
NatSM_and_POCSM <- corr.test(NativeSM.comp, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/NonPOC Social Movements
NatSM_and_NonPOCSM <- corr.test(NativeSM.comp, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Liberal Social Movements
NatSM_and_LiberalSM <- corr.test(NativeSM.comp, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Conservative Social Movements
NatSM_and_ConservSM <- corr.test(NativeSM.comp, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Environmental Social Movements
NatSM_and_EnvirSM <- corr.test(NativeSM.comp, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Women Centered Social Movements
NatSM_and_WomenSM <- corr.test(NativeSM.comp, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Attitudes and Beliefs
NatSM_and_AB <- corr.test(NativeSM.comp, y = att.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Victim Blaming
NatSM_and_VB <- corr.test(NativeSM.comp, y = vicblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/External Factors
NatSM_and_EF <- corr.test(NativeSM.comp, y = externfactors.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Community Blame
NatSM_and_CB <- corr.test(NativeSM.comp, y = commblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Support
NatSM_and_Support <- corr.test(NativeSM.comp, y = sup.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Invisibility
NatSM_and_Invisibility <- corr.test(NativeSM.comp, y = in.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Sovereignty
NatSM_and_Sovereignty <- corr.test(NativeSM.comp, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Race Minimization
NatSM_and_RaceMini <- corr.test(NativeSM.comp, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Cultural Racism
NatSM_and_CRacism <- corr.test(NativeSM.comp, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/Native Dehumanization
NatSM_and_NtvDehum <- corr.test(NativeSM.comp, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/ White Dehumanization
NatSM_and_WhiteDehum <- corr.test(NativeSM.comp, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/ Ambivalent Sexism Inventory
NatSM_and_ASI <- corr.test(NativeSM.comp, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/ Hostile Sexism
NatSM_and_HS <- corr.test(NativeSM.comp, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/ Benevolent Sexism
NatSM_and_BS <- corr.test(NativeSM.comp, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/ Age
NatSM_and_Age <- corr.test(NativeSM.comp, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/ SES
NatSM_and_SES <- corr.test(NativeSM.comp, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#NativeSM/ Liberalism-Conservatism
NatSM_and_LibCon <- corr.test(NativeSM.comp, y = data$LibCon, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)
```
#Knowledge of MMIWG Correlations
```{r}
#MMIWG/Social Movements
MMIWG_and_SM <- corr.test(data$MMIWG, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Native Social Movements
MMIWG_and_NatSM <- corr.test(data$MMIWG, y = NativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Non-Native Social Movements
MMIWG_and_NonNatSM <- corr.test(data$MMIWG, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/POC Social Movements
MMIWG_and_POCSM <- corr.test(data$MMIWG, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/NonPOC Social Movements
MMIWG_and_NonPOCSM <- corr.test(data$MMIWG, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Liberal Social Movements
MMIWG_and_LiberalSM <- corr.test(data$MMIWG, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Conservative Social Movements
MMIWG_and_ConservSM <- corr.test(data$MMIWG, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Environmental Social Movements
MMIWG_and_EnvirSM <- corr.test(data$MMIWG, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Women Centered Social Movements
MMIWG_and_WomenSM <- corr.test(data$MMIWG, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Attitudes and Beliefs
MMIWG_and_AB <- corr.test(data$MMIWG, y = att.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Victim Blaming
MMIWG_and_VB <- corr.test(data$MMIWG, y = vicblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/External Factors
MMIWG_and_EF <- corr.test(data$MMIWG, y = externfactors.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Community Blame
MMIWG_and_CB <- corr.test(data$MMIWG, y = commblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Support
MMIWG_and_Support <- corr.test(data$MMIWG, y = sup.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Invisibility
MMIWG_and_Invisibility <- corr.test(data$MMIWG, y = in.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Sovereignty
MMIWG_and_Sovereignty <- corr.test(data$MMIWG, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Race Minimization
MMIWG_and_RaceMini <- corr.test(data$MMIWG, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Cultural Racism
MMIWG_and_CRacism <- corr.test(data$MMIWG, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/Native Dehumanization
MMIWG_and_NtvDehum <- corr.test(data$MMIWG, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/ White Dehumanization
MMIWG_and_WhiteDehum <- corr.test(data$MMIWG, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/ Ambivalent Sexism Inventory
MMIWG_and_ASI <- corr.test(data$MMIWG, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/ Hostile Sexism
MMIWG_and_HS <- corr.test(data$MMIWG, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/ Benevolent Sexism
MMIWG_and_BS <- corr.test(data$MMIWG, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/ Age
MMIWG_and_Age <- corr.test(data$MMIWG, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/ SES
MMIWG_and_SES <- corr.test(data$MMIWG, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#MMIWG/ Liberalism-Conservatism
MMIWG_and_LibCon <- corr.test(data$MMIWG, y = data$LibCon, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)
```
#Invisibility Correlations
```{r}
#Invisibility/Social Movements
Inv_and_SM <- corr.test(in.com, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Native Social Movements
Inv_and_NatSM <- corr.test(in.com, y = NativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Non-Native Social Movements
Inv_and_NonNatSM <- corr.test(in.com, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/POC Social Movements
Inv_and_POCSM <- corr.test(in.com, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/NonPOC Social Movements
Inv_and_NonPOCSM <- corr.test(in.com, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Liberal Social Movements
Inv_and_LiberalSM <- corr.test(in.com, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Conservative Social Movements
Inv_and_ConservSM <- corr.test(in.com, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Environmental Social Movements
Inv_and_EnvirSM <- corr.test(in.com, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Women Centered Social Movements
Inv_and_WomenSM <- corr.test(in.com, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Attitudes and Beliefs
Inv_and_AB <- corr.test(in.com, y = att.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Victim Blaming
Inv_and_VB <- corr.test(in.com, y = vicblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/External Factors
Inv_and_EF <- corr.test(in.com, y = externfactors.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Community Blame
Inv_and_CB <- corr.test(in.com, y = commblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Support
Inv_and_Support <- corr.test(in.com, y = sup.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Sovereignty
Inv_and_Sovereignty <- corr.test(in.com, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Race Minimization
Inv_and_RaceMini <- corr.test(in.com, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Cultural Racism
Inv_and_CRacism <- corr.test(in.com, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/Native Dehumanization
Inv_and_NtvDehum <- corr.test(in.com, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/ White Dehumanization
Inv_and_WhiteDehum <- corr.test(in.com, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/ Ambivalent Sexism Inventory
Inv_and_ASI <- corr.test(in.com, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/ Hostile Sexism
Inv_and_HS <- corr.test(in.com, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/ Benevolent Sexism
Inv_and_BS <- corr.test(in.com, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/ Age
Inv_and_Age <- corr.test(in.com, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/ SES
Inv_and_SES <- corr.test(in.com, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility/ Liberalism-Conservatism
Inv_and_LibCon <- corr.test(in.com, y = data$LibCon, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)
```

#Violence Against Native Women Correlations
```{r}
#Invisibility of Violence Against NA Women/Social Movements
ViolNA_and_SM <- corr.test(data$IN_Violence, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Native Social Movements
ViolNA_and_NatSM <- corr.test(data$IN_Violence, y = NativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Non-Native Social Movements
ViolNA_and_NonNatSM <- corr.test(data$IN_Violence, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/POC Social Movements
ViolNA_and_POCSM <- corr.test(data$IN_Violence, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/NonPOC Social Movements
ViolNA_and_NonPOCSM <- corr.test(data$IN_Violence, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Liberal Social Movements
ViolNA_and_LiberalSM <- corr.test(data$IN_Violence, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Conservative Social Movements
ViolNA_and_ConservSM <- corr.test(data$IN_Violence, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Environmental Social Movements
ViolNA_and_EnvirSM <- corr.test(data$IN_Violence, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Women Centered Social Movements
ViolNA_and_WomenSM <- corr.test(data$IN_Violence, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Attitudes and Beliefs
ViolNA_and_AB <- corr.test(data$IN_Violence, y = att.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Victim Blaming
ViolNA_and_VB <- corr.test(data$IN_Violence, y = vicblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/External Factors
ViolNA_and_EF <- corr.test(data$IN_Violence, y = externfactors.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Community Blame
ViolNA_and_CB <- corr.test(data$IN_Violence, y = commblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Support
ViolNA_and_Support <- corr.test(data$IN_Violence, y = sup.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Invisibility
ViolNA_and_Invisibility <- corr.test(data$IN_Violence, y = in.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Sovereignty
ViolNA_and_Sovereignty <- corr.test(data$IN_Violence, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Race Minimization
ViolNA_and_RaceMini <- corr.test(data$IN_Violence, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Cultural Racism
ViolNA_and_CRacism <- corr.test(data$IN_Violence, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/Native Dehumanization
ViolNA_and_NtvDehum <- corr.test(data$IN_Violence, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/ White Dehumanization
ViolNA_and_WhiteDehum <- corr.test(data$IN_Violence, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/ Ambivalent Sexism Inventory
ViolNA_and_ASI <- corr.test(data$IN_Violence, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/ Hostile Sexism
ViolNA_and_HS <- corr.test(data$IN_Violence, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/ Benevolent Sexism
ViolNA_and_BS <- corr.test(data$IN_Violence, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/ Age
ViolNA_and_Age <- corr.test(data$IN_Violence, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/ SES
ViolNA_and_SES <- corr.test(data$IN_Violence, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Invisibility of Violence Against NA Women/ Liberalism-Conservatism
ViolNA_and_LibCon <- corr.test(data$IN_Violence, y = data$LibCon, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)
```

#Liberalism/Conservatism Correlations
```{r}
#Liberalism-Conservatism/Social Movements
LibCon_and_SM <- corr.test(data$LibCon, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Native Social Movements
LibCon_and_NatSM <- corr.test(data$LibCon, y = NativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Non-Native Social Movements
LibCon_and_NonNatSM <- corr.test(data$LibCon, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/POC Social Movements
LibCon_and_POCSM <- corr.test(data$LibCon, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/NonPOC Social Movements
LibCon_and_NonPOCSM <- corr.test(data$LibCon, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Liberal Social Movements
LibCon_and_LiberalSM <- corr.test(data$LibCon, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Conservative Social Movements
LibCon_and_ConservSM <- corr.test(data$LibCon, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Environmental Social Movements
LibCon_and_EnvirSM <- corr.test(data$LibCon, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Women Centered Social Movements
LibCon_and_WomenSM <- corr.test(data$LibCon, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Attitudes and Beliefs
LibCon_and_AB <- corr.test(data$LibCon, y = att.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Victim Blaming
LibCon_and_VB <- corr.test(data$LibCon, y = vicblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/External Factors
LibCon_and_EF <- corr.test(data$LibCon, y = externfactors.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Community Blame
LibCon_and_CB <- corr.test(data$LibCon, y = commblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Support
LibCon_and_Support <- corr.test(data$LibCon, y = sup.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Invisibility
LibCon_and_Invisibility <- corr.test(data$LibCon, y = in.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Sovereignty
LibCon_and_Sovereignty <- corr.test(data$LibCon, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Race Minimization
LibCon_and_RaceMini <- corr.test(data$LibCon, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Cultural Racism
LibCon_and_CRacism <- corr.test(data$LibCon, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/Native Dehumanization
LibCon_and_NtvDehum <- corr.test(data$LibCon, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/ White Dehumanization
LibCon_and_WhiteDehum <- corr.test(data$LibCon, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/ Ambivalent Sexism Inventory
LibCon_and_ASI <- corr.test(data$LibCon, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/ Hostile Sexism
LibCon_and_HS <- corr.test(data$LibCon, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/ Benevolent Sexism
LibCon_and_BS <- corr.test(data$LibCon, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/ Age
LibCon_and_Age <- corr.test(data$LibCon, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Liberalism-Conservatism/ SES
LibCon_and_SES <- corr.test(data$LibCon, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

```

#Support for Actions to end MMIWG Correlations
```{r}
#Support/Social Movements
Support_and_SM <- corr.test(sup.com, y = SocialMovements.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Native Social Movements
Support_and_NatSM <- corr.test(sup.com, y = NativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Non-Native Social Movements
Support_and_NonNatSM <- corr.test(sup.com, y = NonNativeSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/POC Social Movements
Support_and_POCSM <- corr.test(sup.com, y = POCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/NonPOC Social Movements
Support_and_NonPOCSM <- corr.test(sup.com, y = NonPOCSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Liberal Social Movements
Support_and_LiberalSM <- corr.test(sup.com, y = LiberalSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Conservative Social Movements
Support_and_ConservSM <- corr.test(sup.com, y = ConservSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Environmental Social Movements
Support_and_EnvirSM <- corr.test(sup.com, y = EnvirSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Women Centered Social Movements
Support_and_WomenSM <- corr.test(sup.com, y = WomenSM.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Attitudes and Beliefs
Support_and_AB <- corr.test(sup.com, y = att.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Victim Blaming
Support_and_VB <- corr.test(sup.com, y = vicblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/External Factors
Support_and_EF <- corr.test(sup.com, y = externfactors.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Community Blame
Support_and_CB <- corr.test(sup.com, y = commblame.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Invisibility
Support_and_Invisibility <- corr.test(sup.com, y = in.com, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Sovereignty
Support_and_Sovereignty <- corr.test(sup.com, y = sov.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Race Minimization
Support_and_RaceMini <- corr.test(sup.com, y = racemini.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Cultural Racism
Support_and_CRacism <- corr.test(sup.com, y = culturalracism.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/Native Dehumanization
Support_and_NtvDehum <- corr.test(sup.com, y = ntvdehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/ White Dehumanization
Support_and_WhiteDehum <- corr.test(sup.com, y = whitedehum.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/ Ambivalent Sexism Inventory
Support_and_ASI <- corr.test(sup.com, y = asi.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/ Hostile Sexism
Support_and_HS <- corr.test(sup.com, y = host.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/ Benevolent Sexism
Support_and_BS <- corr.test(sup.com, y = ben.comp, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/ Age
Support_and_Age <- corr.test(sup.com, y = data$Age.r, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/ SES
Support_and_SES <- corr.test(sup.com, y = data$SES, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)

#Support/ Liberalism-Conservatism
Support_and_LibCon <- corr.test(sup.com, y = data$LibCon, use = "pairwise",method="pearson",adjust="holm", 
alpha=.05,ci=TRUE,minlength=5)
```

#Mutate Data
```{r}
data <- data %>% 
  mutate(Gender = factor(Gender, 
                        labels = c("Male", "Female")),
         BorninUS = factor(BorninUS,
                        labels = c("No", "Yes")),
         SES = factor(SES,
                      labels = c("High School", "Associates/Technical Degree", "BA/BS", "MA/MS", "Doctorate")),
         Citizen = factor(Citizen,
                          labels = c("No", "Yes")),
         LibCon = factor(LibCon,
                         labels = c("Extremely Conservative", "Conservative", "Somewhat Conservative", "Moderate", "Somewhat Liberal", "Liberal", "Extremely Liberal")),
         NewsSource = factor(NewsSource,
                             labels = c("NatTV", "LocalTV", "SocialMedia", "Radio/Podcast", "OnlineBlog", "NatNewspaper", "LocalNewspaper", "PublishedResearch", "WordofMouth", "Unsure")))
```

